---
title: "Exploratory Data Analysis"
author: "James"
date: '2022-07-07'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)

wave_5 <- read_dta("../data/wave-5-(21-mo)/BB2_W5-BIT.dta")
PLS_w4 <- read_excel("../data/wave-4-(18-mo)/PLS_W4_Final.xlsx")
PLS_w6 <- read_excel("../data/wave-6-(24-mo)/PLS_W6.xlsx")
```

# clean w6 pls
```{r}
PLS_w6 <- clean_names(PLS_w6)
glimpse(PLS_w6)
```

```{r}
PLS_w6 <-  PLS_w6 %>% 
  mutate(child_id = as.character(childid),
         par_id = as.character(parid),
        language= as.factor(case_when(
          language == 0 ~ "english",
          language == 1 ~ "spanish"
        )),
        site = as.factor(case_when(
          site == 1 ~ "umd",
          site == 2 ~ "uci"
        )))
```


```{r}
PLS_w6 <- PLS_w6 %>%
  select(child_id, par_id, language, auditory_comprehension_score = plsacss, expressive_communication_score = plsecss, total_score = plsss)
```

# clean w4 pls

```{r}
PLS_w4 <- clean_names(PLS_w4)
```

```{r}
PLS_w4 <-  PLS_w4 %>% 
  mutate(child_id = as.character(childid),
         par_id = as.character(parid),
        language= as.factor(case_when(
          language == 0 ~ "english",
          language == 1 ~ "spanish"
        )),
        site = as.factor(case_when(
          site == 1 ~ "umd",
          site == 2 ~ "uci"
        )))
```


```{r}
PLS_w4 <- PLS_w4 %>%
  select(child_id, par_id, language, auditory_comprehension_score = plsacss, expressive_communication_score = plsecss, total_score = plsss)
```


# clean BIT of wave 5

```{r}
wave_5 <- wave_5 %>% 
  mutate(child_id = as.character(childid),
          par_id = as.character(parid),
          wave = as.factor(wave),
          pargen = as.factor(pargen),
          site = as.factor(site),
          bit01 = as.factor(case_when(
            bit01 == 0 ~ "Not true/Rarely",
            bit01 == 1 ~ "Somewhat true/Sometimes",
            bit01 == 2 ~ "Very true/Often"
          )),
          bit02 = as.factor(case_when(
						bit02 == 0 ~ "Not true/Rarely",
						bit02 == 1 ~ "Somewhat true/Sometimes",
						bit02 == 2 ~ "Very true/Often")),
          bit03 = as.factor(case_when(
						bit03 == 0 ~ "Not true/Rarely",
						bit03 == 1 ~ "Somewhat true/Sometimes",
						bit03 == 2 ~ "Very true/Often")),
          bit04 = as.factor(case_when(
						bit04 == 0 ~ "Not true/Rarely",
						bit04 == 1 ~ "Somewhat true/Sometimes",
						bit04 == 2 ~ "Very true/Often")),
          bit05 = as.factor(case_when(
						bit05 == 0 ~ "Not true/Rarely",
						bit05 == 1 ~ "Somewhat true/Sometimes",
						bit05 == 2 ~ "Very true/Often")),
          bit06 = as.factor(case_when(
						bit06 == 0 ~ "Not true/Rarely",
						bit06 == 1 ~ "Somewhat true/Sometimes",
						bit06 == 2 ~ "Very true/Often")),
          bit07 = as.factor(case_when(
						bit07 == 0 ~ "Not true/Rarely",
						bit07 == 1 ~ "Somewhat true/Sometimes",
						bit07 == 2 ~ "Very true/Often")),
          bit08 = as.factor(case_when(
						bit08 == 0 ~ "Not true/Rarely",
						bit08 == 1 ~ "Somewhat true/Sometimes",
						bit08 == 2 ~ "Very true/Often")),
          bit08txt = as.character(bit08txt),
          bit08txt_e = as.character(bit08txt_e),
          bit09 = as.factor(case_when(
						bit09 == 0 ~ "Not true/Rarely",
						bit09 == 1 ~ "Somewhat true/Sometimes",
						bit09 == 2 ~ "Very true/Often")),
          bit10 = as.factor(case_when(
						bit10 == 0 ~ "Not true/Rarely",
						bit10 == 1 ~ "Somewhat true/Sometimes",
						bit10 == 2 ~ "Very true/Often")),
          bit11 = as.factor(case_when(
						bit11 == 0 ~ "Not true/Rarely",
						bit11 == 1 ~ "Somewhat true/Sometimes",
						bit11 == 2 ~ "Very true/Often")),
          bit12 = as.factor(case_when(
						bit12 == 0 ~ "Not true/Rarely",
						bit12 == 1 ~ "Somewhat true/Sometimes",
						bit12 == 2 ~ "Very true/Often")),
          bit13 = as.factor(case_when(
						bit13 == 0 ~ "Not true/Rarely",
						bit13 == 1 ~ "Somewhat true/Sometimes",
						bit13 == 2 ~ "Very true/Often")),
          bit14 = as.factor(case_when(
						bit14 == 0 ~ "Not true/Rarely",
						bit14 == 1 ~ "Somewhat true/Sometimes",
						bit14 == 2 ~ "Very true/Often")),
          bit15 = as.factor(case_when(
						bit15 == 0 ~ "Not true/Rarely",
						bit15 == 1 ~ "Somewhat true/Sometimes",
						bit15 == 2 ~ "Very true/Often")),
          bit16 = as.factor(case_when(
						bit16 == 0 ~ "Not true/Rarely",
						bit16 == 1 ~ "Somewhat true/Sometimes",
						bit16 == 2 ~ "Very true/Often")),
          bit17 = as.factor(case_when(
						bit17 == 0 ~ "Not true/Rarely",
						bit17 == 1 ~ "Somewhat true/Sometimes",
						bit17 == 2 ~ "Very true/Often")),
          bit18 = as.factor(case_when(
						bit18 == 0 ~ "Not true/Rarely",
						bit18 == 1 ~ "Somewhat true/Sometimes",
						bit18 == 2 ~ "Very true/Often")),
          bit19 = as.factor(case_when(
						bit19 == 0 ~ "Not true/Rarely",
						bit19 == 1 ~ "Somewhat true/Sometimes",
						bit19 == 2 ~ "Very true/Often")),
          bit20 = as.factor(case_when(
						bit20 == 0 ~ "Not true/Rarely",
						bit20 == 1 ~ "Somewhat true/Sometimes",
						bit20 == 2 ~ "Very true/Often")),
          bit21 = as.factor(case_when(
						bit21 == 0 ~ "Not true/Rarely",
						bit21 == 1 ~ "Somewhat true/Sometimes",
						bit21 == 2 ~ "Very true/Often")),
          bit22 = as.factor(case_when(
						bit22 == 0 ~ "Not true/Rarely",
						bit22 == 1 ~ "Somewhat true/Sometimes",
						bit22 == 2 ~ "Very true/Often")),
          bit23 = as.factor(case_when(
						bit23 == 0 ~ "Not true/Rarely",
						bit23 == 1 ~ "Somewhat true/Sometimes",
						bit23 == 2 ~ "Very true/Often")),
          bit24 = as.factor(case_when(
						bit24 == 0 ~ "Not true/Rarely",
						bit24 == 1 ~ "Somewhat true/Sometimes",
						bit24 == 2 ~ "Very true/Often")),
          bit25 = as.factor(case_when(
						bit25 == 0 ~ "Not true/Rarely",
						bit25 == 1 ~ "Somewhat true/Sometimes",
						bit25 == 2 ~ "Very true/Often")),
          bit26 = as.factor(case_when(
						bit26 == 0 ~ "Not true/Rarely",
						bit26 == 1 ~ "Somewhat true/Sometimes",
						bit26 == 2 ~ "Very true/Often")),
          bit27 = as.factor(case_when(
						bit27 == 0 ~ "Not true/Rarely",
						bit27 == 1 ~ "Somewhat true/Sometimes",
						bit27 == 2 ~ "Very true/Often")),
          bit28 = as.factor(case_when(
						bit28 == 0 ~ "Not true/Rarely",
						bit28 == 1 ~ "Somewhat true/Sometimes",
						bit28 == 2 ~ "Very true/Often")),
          bit29 = as.factor(case_when(
						bit29 == 0 ~ "Not true/Rarely",
						bit29 == 1 ~ "Somewhat true/Sometimes",
						bit29 == 2 ~ "Very true/Often")),
          bit30 = as.factor(case_when(
						bit30 == 0 ~ "Not true/Rarely",
						bit30 == 1 ~ "Somewhat true/Sometimes",
						bit30 == 2 ~ "Very true/Often")),
          bit31 = as.factor(case_when(
						bit31 == 0 ~ "Not true/Rarely",
						bit31 == 1 ~ "Somewhat true/Sometimes",
						bit31 == 2 ~ "Very true/Often")),
          bit32 = as.factor(case_when(
						bit32 == 0 ~ "Not true/Rarely",
						bit32 == 1 ~ "Somewhat true/Sometimes",
						bit32 == 2 ~ "Very true/Often")),
          bit33 = as.factor(case_when(
						bit33 == 0 ~ "Not true/Rarely",
						bit33 == 1 ~ "Somewhat true/Sometimes",
						bit33 == 2 ~ "Very true/Often")),
          bit34 = as.factor(case_when(
						bit34 == 0 ~ "Not true/Rarely",
						bit34 == 1 ~ "Somewhat true/Sometimes",
						bit34 == 2 ~ "Very true/Often")),
          bit35 = as.factor(case_when(
						bit35 == 0 ~ "Not true/Rarely",
						bit35 == 1 ~ "Somewhat true/Sometimes",
						bit35 == 2 ~ "Very true/Often")),
          bit36 = as.factor(case_when(
						bit36 == 0 ~ "Not true/Rarely",
						bit36 == 1 ~ "Somewhat true/Sometimes",
						bit36 == 2 ~ "Very true/Often")),
          bit36txt = as.character(bit36txt),
          bit36txt_e = as.character(bit36txt_e),
          bit37 = as.factor(case_when(
						bit37 == 0 ~ "Not true/Rarely",
						bit37 == 1 ~ "Somewhat true/Sometimes",
						bit37 == 2 ~ "Very true/Often")),
          bit37txt = as.character(bit37txt),
          bit37txt_e = as.character(bit37txt_e),
          bit38 = as.factor(case_when(
						bit38 == 0 ~ "Not true/Rarely",
						bit38 == 1 ~ "Somewhat true/Sometimes",
						bit38 == 2 ~ "Very true/Often")),
          bit39 = as.factor(case_when(
						bit39 == 0 ~ "Not true/Rarely",
						bit39 == 1 ~ "Somewhat true/Sometimes",
						bit39 == 2 ~ "Very true/Often")),
          bit40 = as.factor(case_when(
						bit40 == 0 ~ "Not true/Rarely",
						bit40 == 1 ~ "Somewhat true/Sometimes",
						bit40 == 2 ~ "Very true/Often")),
          bit41 = as.factor(case_when(
						bit41 == 0 ~ "Not true/Rarely",
						bit41 == 1 ~ "Somewhat true/Sometimes",
						bit41 == 2 ~ "Very true/Often")),
          bit41txt = as.character(bit41txt),
          bit41txt_e = as.character(bit41txt_e),
          bit42 = as.factor(case_when(
						bit42 == 0 ~ "Not true/Rarely",
						bit42 == 1 ~ "Somewhat true/Sometimes",
						bit42 == 2 ~ "Very true/Often")),
          bit42txt = as.character(bit42txt),
          bit42txt_e = as.character(bit42txt_e),
          bit43a = as.factor(case_when(
						bit43a == 1 ~ "Not worried at all",
						bit43a == 2 ~ "A little worried",
						bit43a == 3 ~ "Worried",
						bit43a == 4 ~ "Very worried")),
          bit43b = as.factor(case_when(
						bit43b == 1 ~ "Not worried at all",
						bit43b == 2 ~ "A little worried",
						bit43b == 3 ~ "Worried",
						bit43b == 4 ~ "Very worried")),
          BITcompnic = as.integer(BITcompnic),
          BITcompts = as.integer(BITcompts),
          BITcompavg = as.double(BITcompavg),
          BITprobnic = as.integer(BITprobnic),
          BITprobts = as.integer(BITprobts),
          BITprobavg = as.double(BITprobavg),
          BITcomp_cut = as.integer(BITcomp_cut),
          BITprob_cut = as.integer(BITprob_cut))
```

## remove redundant variables

```{r}
wave_5 <- wave_5 %>% 
  select(-c(childid, parid))
```

# Join all data base on PLS and BITSEA

## Import data

```{r}
BIT_w2 <- readRDS(file="../data/BITSEA_wave_2.dta")
BIT_w6 <- readRDS(file="../data/BITSEA_wave_6.dta")
PLS_w1 <- readRDS(file="../data/PLS_wave_1.dta")
media_w1 <- readRDS(file="../data/media_wave_1.dta")
demography <- readRDS(file="../data/demographic_dataset.dta")
```

## join them

```{r}
PLS_w4 <- PLS_w4 %>% 
  mutate(wave = as.factor(4))
PLS_w6 <- PLS_w6 %>% 
  mutate(wave = as.factor(6))
```

#### clean demography
```{r}
demography <- demography %>% 
  select(-matches(".*\\.(x|y)")) %>% 
  glimpse()
```
### join PLS

```{r}
PLS_data <- full_join(PLS_w1,PLS_w4) %>%
            full_join(PLS_w6) %>% 
            select(-language, -father)
```
### join BITSEA

```{r}
BIT_data <- full_join(BIT_w2,BIT_w6) %>%
            full_join(wave_5) %>% 
            select(-matches("^bit\\d"), -c("svdt","version","language"))
```

### join Media tech
```{r}
media_w1 %>% 
  select(-matches(".*\\.(x|y)"))
```


```{r}
media_data <- media_w1

media_data <- media_data %>% 
  select(-matches("^q\\d.*"))

glimpse(media_data)
```


# Convert data to long type

## BITSEA to long DOES NOT WORK because of duplicate child_id

```{r}
BIT_long <- BIT_data %>% 
  select(-c(svdt_31_BIT_w2,language_31_BIT_w2,BITcompnic,BITprobnic,site,wave5_bit_notes))


tmp <- filter(BIT_long, wave == 6) %>%
  select(-c(wave,pargen)) %>% 
  rename_at(vars(-par_id, -child_id), ~ paste0(., '.6'))

BIT_long <- filter(BIT_long,wave == 2) %>% 
        full_join(
            filter(BIT_long, wave == 5),
            by=c("par_id", "child_id"),
            suffix = c(".2", ".5")) %>% 
        select(-matches("(wave|pargen).*")) %>% 
        full_join(tmp, 
            by=c("par_id", "child_id"), 
            suffix = c(".error", ".error"))

BIT_long <- BIT_long %>%
  select(par_id, child_id, everything())
```

#### BITSEA for FATHER/mother and avg scores only
```{r}
BIT_long_father <- BIT_long %>% 
  filter(par_id >= 30000) %>% 
  select(matches(".+_id$"), matches(".+avg.+"))

BIT_long_mother <- BIT_long %>% 
  filter(par_id < 30000) %>% 
  select(matches(".+_id$"), matches(".+avg.+"))
```

```{r}
tmp_f <- function(df){
  df <- as.data.frame(df) %>% 
    reshape(varying = c("BITcompavg.2", "BITcompavg.5", "BITcompavg.6", "BITprobavg.2", "BITprobavg.5", "BITprobavg.6"),
    v.names = c("BITcompavg","BITprobavg"),
    timevar = "wave",
    times = c("2","5","6"),
    direction = "long")
  return (df)
}
BIT_long_father <-  tmp_f(BIT_long_father)
BIT_long_mother <-  tmp_f(BIT_long_mother)
```


#### BITSEA for avg of parents and avg scores only
```{r}
BIT_long_par <- BIT_long %>%
  select(matches(".+_id$"), matches(".+avg.+")) %>% 
  group_by(child_id) %>% 
  summarize_if(is.numeric, mean, na.rm = TRUE)
```
```{r}
BIT_long_par <- tmp_f(BIT_long_par)
```

## PLS to long data

```{r}
PLS_tmp <- PLS_data

tmp <- filter(PLS_tmp, wave == 6) %>%
  select(-c(wave)) %>% 
  rename_at(vars(-par_id, -child_id), ~ paste0(., '.6'))

PLS_tmp <- filter(PLS_tmp,wave == 1) %>% 
        full_join(
            filter(PLS_tmp, wave == 4),
            by=c("par_id", "child_id"),
            suffix = c(".1", ".4")) %>% 
        select(-matches("(wave).*")) %>% 
        full_join(tmp, 
            by=c("par_id", "child_id"), 
            suffix = c(".error", ".error"))

PLS_tmp <- as.data.frame(PLS_tmp) %>%
  filter(par_id < 30000)

```

### by auditory_comprehension_score, expressive_communication_score, total score

```{r}
PLS_long <- reshape(PLS_tmp,
  varying = c("auditory_comprehension_score.1", "auditory_comprehension_score.4",
              "auditory_comprehension_score.6","expressive_communication_score.1",
              "expressive_communication_score.4","expressive_communication_score.6",
              "total_score.1", "total_score.4", "total_score.6"), 
  v.names = c("auditory_comprehension_score","expressive_communication_score",
              "total_score"),
  timevar = "wave",
  times = c("1","4","6"),
  direction = "long")
```

# save data back to file


```{r}
saveRDS(PLS_long, file="../data/PLS_long.dta")
saveRDS(BIT_long_par, file="../data/BIT_long_par.dta")
saveRDS(BIT_long_father, file="../data/BIT_long_father.dta")
saveRDS(BIT_long_mother, file="../data/BIT_long_mother.dta")
saveRDS(media_data, file="../data/media_data.dta")
saveRDS(demography, file="../data/demography.dta")
```

# load data back
```{r}
PLS_long <- readRDS(file="../data/PLS_long.dta")
BIT_long_par <- readRDS(file="../data/BIT_long_par.dta")
BIT_long_father <- readRDS(file="../data/BIT_long_father.dta")
BIT_long_mother <- readRDS(file="../data/BIT_long_mother.dta")
media_data <- readRDS(file="../data/media_data.dta")
demography <- readRDS(file="../data/demography.dta")
```
