```{r}
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)
library(ggcorrplot)
library(patchwork)
```

```{r}
model_w2 <- readRDS(file="../data/model_w2.dta")
model_w6 <- readRDS(file="../data/model_w6.dta")
valuable_dataset <- readRDS(file="../data/valuable_dataset.dta")
```


# Chandra

## Bootstrap function

```{r}
# bootstrap function
bootstrap <- function(col, func, num) {
  temp <- numeric(num)
  for (i in 1:num) {
    temp[i] <- func(sample(col, length(col), replace=TRUE), na.rm = TRUE)
  }
  ci <- quantile(temp, prob = c(0.025, 0.975), na.rm = TRUE)
  list(est=func(temp), ci=ci)
}

# example usage
mean_diff <- bootstrap(valuable_dataset$digital_babysitting, mean, 1000)

mean_diff
```

## Subsetted datasets

```{r}
demographics <- valuable_dataset %>% 
  select(-c(n_devices,
          tv_exposure,
          solo,
          passive,
          coop,
          mealtimes,
          behavior_management,
          positive_beliefs_media,
          educational_benefits,
          digital_babysitting,
          daily_use))

head(demographics)

predictors <- valuable_dataset %>% 
  select(
    par_id,
    child_id,
    MT_n_devices = n_devices, 
    MT_tv_exposure = tv_exposure, 
    MT_solo = solo, 
    MT_passive = passive, 
    MT_coop = coop, 
    MT_mealtimes = mealtimes, 
    MT_behavior_management = behavior_management, 
    MT_positive_beliefs_media = positive_beliefs_media,
    MT_educational_benefits = educational_benefits,
    MT_digital_babysitting = digital_babysitting,
    MT_daily_use = daily_use)

head(predictors)

responses <- model_w2 %>% 
  inner_join(model_w6, by = c("par_id", "child_id"), suffix = c("_w2", "_w6")) %>% 
  inner_join(valuable_dataset, by = c("par_id", "child_id")) %>% 
  select(child_id, par_id, matches("^BIT", ignore.case = FALSE)) %>% 
  mutate(BITcompavg_diff = BITcompavg_w6 - BITcompavg_w2,
         BITprobavg_diff = BITprobavg_w6 - BITprobavg_w2)
  
head(responses)

```

## Average difference with 95% CI

```{r}
# average difference of problem and competence score between wave 6 and wave 2
# with 95% CI through bootstrap
responses %>%
  summarize(mean_prob_score = mean(BITprobavg_diff, na.rm = TRUE),
            mean_comp_score = mean(BITcompavg_diff, na.rm = TRUE))

bootstrap(responses$BITprobavg_diff, mean, 10000)
bootstrap(responses$BITcompavg_diff, mean, 10000)
```

# Correlation matrix for problem score

```{r}
responses %>% 
  inner_join(predictors, by = c("par_id", "child_id")) %>% 
  select(BITprobavg_w2,
         matches("^MT", ignore.case = FALSE)) %>% 
  cor(use = "complete.obs") %>% 
  ggcorrplot(hc.order = TRUE, type = "lower", outline.color = "white")
```

## Correlation matrix for competance score

```{r}
responses %>% 
  inner_join(predictors, by = c("par_id", "child_id")) %>% 
  select(BITcompavg_w2,
         matches("^MT", ignore.case = FALSE)) %>% 
  cor(use = "complete.obs") %>% 
  ggcorrplot(hc.order = TRUE, type = "lower", outline.color = "white")
```

## daily use vs problem score - income

```{r}
responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  ggplot(aes(MT_daily_use, BITprobavg_w2)) +
  labs(title = "Daily Media Usage vs Social Problem Score",
       x = "Daily use average score",
       y = "Social problem average score") +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~household_income_categorical)
  
```

## daily use vs problem score - highest degree completed

```{r}
responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  ggplot(aes(MT_daily_use, BITprobavg_w2)) +
  labs(title = "Daily Media Usage vs Social Problem Score",
       x = "Daily use average score",
       y = "Social problem average score") +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~highest_degree_completed)
```

## daily use vs problem score - problem cuttoff

```{r}
responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  mutate(`Problem Cutoff` = case_when(
    BITprob_cut_w2 == 0 ~ "Problem Score < 13",
    BITprob_cut_w2 == 1 ~ "Problem Score >= 13")) %>% 
  ggplot(aes(MT_daily_use, BITprobavg_w2, color = `Problem Cutoff`)) +
  labs(title = "Daily Media Usage vs Social Problem Score",
       x = "Daily use average score",
       y = "Social problem average score") +
  geom_point() +
  geom_smooth(method = "lm")
```

## daily use vs problem score faceted by income grouped by problem cutoff

```{r}
responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  mutate(`Problem Cutoff` = case_when(
    BITprob_cut_w2 == 0 ~ "Problem Score < 13",
    BITprob_cut_w2 == 1 ~ "Problem Score >= 13")) %>% 
  ggplot(aes(MT_daily_use, BITprobavg_w2, color = `Problem Cutoff`)) +
  labs(title = "Daily Media Usage vs Social Problem Score",
       x = "Daily use average score",
       y = "Social problem average score") +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~household_income_categorical)
```

## solo use vs problem average score

```{r}
solo_2 <- responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  ggplot(aes(MT_solo, BITprobavg_w2)) +
  labs(title = "Solo Media Usage vs Social Problem Score",
       x = "Solo media use\nWave 2",
       y = "Social problem average score") +
  geom_jitter() +
  geom_smooth(method = "lm")

solo_2
```

## coop use vs problem average score

```{r}
coop_2 <- responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  ggplot(aes(MT_coop, BITprobavg_w2)) +
  labs(title = "Co-op Media Usage vs Social Problem Score",
       x = "Co-op media use\nWave 2",
       y = "Social problem average score") +
  geom_jitter() +
  geom_smooth(method = "lm")

coop_2
```

## solo and coop use side by side comparison

```{r}
solo_2 + coop_2
```
## daily use vs competence comparison

```{r}
responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  ggplot(aes(MT_daily_use, BITcompavg_w2)) +
  labs(title = "Daily Media Usage vs Social Competence Score",
       x = "Daily use average score",
       y = "Social competence average score") +
  geom_jitter() +
  geom_smooth(method = "lm")

```

## coop use vs competence comparison

```{r}
responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  ggplot(aes(MT_coop, BITcompavg_w2)) +
  labs(title = "Co-op Usage vs Social Competence Score",
       x = "Co-op use average score",
       y = "Social competence average score") +
  geom_point() +
  geom_smooth(method = "lm")
```
## solo use vs problem average score - wave 6

```{r}
solo_6 <- responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  ggplot(aes(MT_solo, BITprobavg_w6)) +
  labs(title = "Solo Media Usage vs Social Problem Score",
       x = "Solo media use\nWave 6",
       y = "Social problem average score") +
  geom_jitter() +
  geom_smooth(method = "lm")

solo_6
```

## coop use vs problem average score - wave 6

```{r}
coop_6 <- responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  ggplot(aes(MT_coop, BITprobavg_w6)) +
  labs(title = "Co-op Media Usage vs Social Problem Score",
       x = "Co-op media use\nWave 6",
       y = "Social problem average score") +
  geom_jitter() +
  geom_smooth(method = "lm")

coop_6
```

## solo and coop use side by side comparison - wave 6
```{r}
solo_6 + coop_6
```

## solo and coop comparisons between wave 2 and 6

```{r}
(solo_2 + coop_2) / (solo_6 + coop_6)
```

