```{r}
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)
```

```{r}
model_w2 <- readRDS(file="../data/model_w2.dta")
model_w6 <- readRDS(file="../data/model_w6.dta")
valuable_dataset <- readRDS(file="../data/valuable_dataset.dta")
```

# James

## preparing

- numeric:
  * w1: n_devices, tv_exposure, solo, passive, coop, mealtimes, behavior_management, positive_beliefs_media, educational_benefits, digital_babysitting, daily_use, auditory_comprehension_score, expressive_communication_score, total_score, household_income_numerical
  * w2: BITcompnic, BITcompts, BITcompavg, BITprobnic, BITprobts, BITprobavg
  * w6: BITcompnic, BITcompts, BITcompavg, BITprobnic, BITprobts, BITprobavg

- categorical:
  * w1: degree_cert_in_prog, parenting_class_taken, highest_degree_completed, years_school_complete, us_education, education_location, span_lang_form, father, data_site, par_ethnicity, par_us_born, par_language, chi_girl, birth_time, planned_preg, chi_ethnicity, chi_par_lang, relatives_lang, father, language, state_welfare, unemployment_insurance, food_stamp, wic, child_support, ssi_and_ssdi, adoption_assistance, utility_assistance, childcare_subsidy, vertan_benefit, medical_assistance, none, other, assistance, par_gen, household_others, marital_status, recieve_childcare, childcare_center, homebased_care, relative_care, other_care, par_gen, household_income_categorical, employment_status, enough_money_clothes, enough_money_food, enough_money_medical_care, bill_difficulty, father, speaking_english, reading_english, writing_english, understanding_english, english_level
  * w2: BITcomp_cut, BITprob_cut
  * w6: BITcomp_cut, BITprob_cut

## For loop

```{r}
w1_num <- list("n_devices" , "tv_exposure" , "solo" , "passive" , "coop" , "mealtimes" , "behavior_management" , "positive_beliefs_media" , "educational_benefits" , "digital_babysitting" , "daily_use" , "auditory_comprehension_score" , "expressive_communication_score" , "total_score" , "household_income_numerical")
w2_num <- list("BITcompnic_w2", "BITcompts_w2", "BITcompavg_w2", "BITprobnic_w2", "BITprobts_w2", "BITprobavg_w2")
w6_num <- list("BITcompnic_w6", "BITcompts_w6", "BITcompavg_w6", "BITprobnic_w6", "BITprobts_w6", "BITprobavg_w6")

w1_cat <- list("degree_cert_in_prog" , "parenting_class_taken" , "highest_degree_completed" , "years_school_complete" , "us_education" , "education_location" , "span_lang_form" , "father" , "data_site" , "par_ethnicity" , "par_us_born" , "par_language" , "chi_girl" , "birth_time" , "planned_preg" , "chi_ethnicity" , "chi_par_lang" , "relatives_lang" , "father" , "language" , "state_welfare" , "unemployment_insurance" , "food_stamp" , "wic" , "child_support" , "ssi_and_ssdi" , "adoption_assistance" , "utility_assistance" , "childcare_subsidy" , "vertan_benefit" , "medical_assistance" , "none" , "other" , "assistance" , "par_gen" , "household_others" , "marital_status" , "recieve_childcare" , "childcare_center" , "homebased_care" , "relative_care" , "other_care" , "par_gen" , "household_income_categorical" , "employment_status" , "enough_money_clothes" , "enough_money_food" , "enough_money_medical_care" , "bill_difficulty" , "father" , "speaking_english" , "reading_english" , "writing_english" , "understanding_english" , "english_level")
w2_cat <- list("BITcomp_cut_w2" , "BITprob_cut_w2")
w6_cat <- list("BITcomp_cut_w6" , "BITprob_cut_w6")
```
#### Merge all three datasets

```{r}
model_full <- full_join(model_w6, model_w2, by=c("par_id", "child_id"), suffix = c("_w6", "_w2")) %>% 
  full_join(valuable_dataset, by=c("par_id", "child_id"), suffix = c("_w62", "_w1"))
```


#### numeric for w2 and w6


##### point for w2 and w6
```{r}
for (i in w2_num){
  for (j in w6_num){
    plot <- ggplot(model_full, 
              aes_string(x = i, 
                         y = j))
    print(plot + geom_jitter())
    print(plot + geom_smooth())
  }
}
```
##### multiplot function
```{r}
multiplot = function(data, list_col, plot_type){
  list_plot <- list()
  counter = 0
  for (i in list_col){
    tmp <- ggplot(data, 
                  aes_string(x = i)) +
                  plot_type
    counter = counter + 1
    list_plot[[counter]] <- tmp
  }
  return(list_plot)
}
```

#### numeric for w1 and w2
```{r}
for (i in w1_num){
  for (j in w2_num){
    plot <- ggplot(model_full, 
              aes_string(x = i, 
                         y = j))
    print(plot + geom_point())
  }
}
```


##### compare w2 and w6


```{r}
hist1 <- multiplot(model_full, w2_num, geom_histogram())
hist2 <- multiplot(model_full, w6_num, geom_histogram())

for (i in 1:length(w2_num)) {
  print(hist1[i])
  print(hist2[i])
}

```

#### something

