```{r}
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)
library(ggcorrplot)
```

```{r}
model_w2 <- readRDS(file="../data/model_w2.dta")
model_w6 <- readRDS(file="../data/model_w6.dta")
valuable_dataset <- readRDS(file="../data/valuable_dataset.dta")
```

# Deborah

# Aubree

```{r}
# Read in Data 
wave_2 <- read_dta("../data/wave-2-(12-mo)/31_BIT_w2.dta")
wave_6 <- read_dta("../data/wave-6-(24-mo)/BB2_W6_BIT.dta")
```

```{r}
### assessing bit12 variable (response variable) (model_w2 data set)
## possible predictors 
# bill_difficulty (income_w1 data)
# employment_status (income_w1 data)
# household_income_numerical (income_w1 data)
# recieve_childcare (access_to_childcare_w1 data)
# household_others (access_to_childcare_w1 data)
# assistance (public_assistance_w1)
# highest_degree_completed (parent_edu_eng data)
# english_level (parent_edu_eng data)
```

```{r}
# Do joins here 
mod_2_and_income_w1 <- inner_join(model_w2, income_w1, 
                                  by=c("child_id", "par_id"))
mod_2_and_income_w1 <- mod_2_and_income_w1 %>% 
  mutate(bit12 = as.factor(case_when(
						bit12 == "Not true/Rarely" ~ 0 ,
						bit12 == "Somewhat true/Sometimes" ~ 1,
						bit12 == "Very true/Often" ~ 2)))
```

```{r}
# bill_difficulty (income_w1 data)
counts_of_response = c(25, 126, 91, 31, 101)
  ggplot(mod_2_and_income_w1, aes(x = bit12)) + 
  geom_bar(aes(fill = bill_difficulty, position = "dodge", stat = "identity"))
## need to make next to each other and not stacked 
```

```{r}
# household_income_numerical (income_w1 data)
library(RColorBrewer)
mod_2_and_income_w1 %>% 
  ggplot(aes(x = bit12, 
             y = household_income_numerical)) + 
  geom_boxplot() + 
  scale_y_binned(limits = c(0, 100000)) 
```

```{r}
# employment_status (income_w1 data)
library(reshape2)


mod_2_and_income_w1 %>% 
  ggplot(aes(x = bit12, fill = employment_status)) + 
  geom_bar()
```

# Daily Use vs. Problem Score - Parenting Class Taken (Y/N)
```{r}
responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  ggplot(aes(MT_daily_use, BITprobavg_w2)) +
  labs(title = "Daily Media Usage vs Social Problem Score Clustered by Parenting Class",
       x = "Daily use average score",
       y = "Social problem average score") +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~parenting_class_taken)
```




# Chandra
## Bootstrap function
```{r}
# bootstrap function
bootstrap <- function(col, func, num) {
  temp <- numeric(num)
  for (i in 1:num) {
    temp[i] <- func(sample(col, length(col), replace=TRUE), na.rm = TRUE)
  }
  ci <- quantile(temp, prob = c(0.025, 0.975), na.rm = TRUE)
  list(est=func(temp), ci=ci)
}

# example usage
mean_diff <- bootstrap(valuable_dataset$digital_babysitting, mean, 1000)

mean_diff
```
# Interpretation 
We are 95% confident that the score assigned for the variable 
"digital_babysitting" increases overtime between 1.52 points and 1.69 
points. 


## Subsetted datasets
```{r}
demographics <- valuable_dataset %>% 
  select(-c(n_devices,
          tv_exposure,
          solo,
          passive,
          coop,
          mealtimes,
          behavior_management,
          positive_beliefs_media,
          educational_benefits,
          digital_babysitting,
          daily_use))

head(demographics)

predictors <- valuable_dataset %>% 
  select(
    par_id,
    child_id,
    MT_n_devices = n_devices, 
    MT_tv_exposure = tv_exposure, 
    MT_solo = solo, 
    MT_passive = passive, 
    MT_coop = coop, 
    MT_mealtimes = mealtimes, 
    MT_behavior_management = behavior_management, 
    MT_positive_beliefs_media = positive_beliefs_media,
    MT_educational_benefits = educational_benefits,
    MT_digital_babysitting = digital_babysitting,
    MT_daily_use = daily_use)

head(predictors)

responses <- model_w2 %>% 
  inner_join(model_w6, by = c("par_id", "child_id"), suffix = c("_w2", "_w6")) %>% 
  inner_join(valuable_dataset, by = c("par_id", "child_id")) %>% 
  select(child_id, par_id, matches("^BIT", ignore.case = FALSE)) %>% 
  mutate(BITcompavg_diff = BITcompavg_w6 - BITcompavg_w2,
         BITprobavg_diff = BITprobavg_w6 - BITprobavg_w2)
  
head(responses)

```

## Average difference with 95% CI
```{r}
# average difference of problem and competence score between wave 6 and wave 2
# with 95% CI through bootstrap
responses %>%
  summarize(mean_prob_score = mean(BITprobavg_diff, na.rm = TRUE),
            mean_comp_score = mean(BITcompavg_diff, na.rm = TRUE))

bootstrap(responses$BITprobavg_diff, mean, 10000)
bootstrap(responses$BITcompavg_diff, mean, 10000)
```

# Correlation matrix for problem score

```{r}
responses %>% 
  inner_join(predictors, by = c("par_id", "child_id")) %>% 
  select(BITprobavg_w2,
         matches("^MT", ignore.case = FALSE)) %>% 
  cor(use = "complete.obs") %>% 
  ggcorrplot(hc.order = TRUE, type = "lower", outline.color = "white")
```

## Correlation matrix for competance score

```{r}
responses %>% 
  inner_join(predictors, by = c("par_id", "child_id")) %>% 
  select(BITcompavg_w2,
         matches("^MT", ignore.case = FALSE)) %>% 
  cor(use = "complete.obs") %>% 
  ggcorrplot(hc.order = TRUE, type = "lower", outline.color = "white")
```

## daily use vs problem score - income

```{r}
responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  ggplot(aes(MT_daily_use, BITprobavg_w2)) +
  labs(title = "Daily Media Usage vs Social Problem Score Clustered by Income",
       x = "Daily use average score",
       y = "Social problem average score") +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~household_income_categorical)
  
```
## daily use vs problem score - highest degree completed
```{r}
responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  ggplot(aes(MT_daily_use, BITprobavg_w2)) +
  labs(title = "Daily Media Usage vs Social Problem Score Clustered by Education",
       x = "Daily use average score",
       y = "Social problem average score") +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~highest_degree_completed)
```
## daily use vs problem score - problem cuttoff
```{r}
responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  mutate(`Problem Cutoff` = case_when(
    BITprob_cut_w2 == 0 ~ "Problem Score < 13",
    BITprob_cut_w2 == 1 ~ "Problem Score >= 13")) %>% 
  ggplot(aes(MT_daily_use, BITprobavg_w2, color = `Problem Cutoff`)) +
  labs(title = "Daily Media Usage vs Social Problem Score",
       x = "Daily use average score",
       y = "Social problem average score") +
  geom_point() +
  geom_smooth(method = "lm")
```
## daily use vs problem score faceted by income grouped by problem cutoff
```{r}
responses %>%
  inner_join(predictors, by = c("par_id", "child_id")) %>%
  inner_join(demographics, by = c("par_id", "child_id")) %>%
  mutate(`Problem Cutoff` = case_when(
    BITprob_cut_w2 == 0 ~ "Problem Score < 13",
    BITprob_cut_w2 == 1 ~ "Problem Score >= 13")) %>% 
  ggplot(aes(MT_daily_use, BITprobavg_w2, color = `Problem Cutoff`)) +
  labs(title = "Daily Media Usage vs Social Problem Score",
       x = "Daily use average score",
       y = "Social problem average score") +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~household_income_categorical)
```


# Nick

predictors : n_devices, tv_exposure, digital_babysitting, daily_use, parenting_class_taken, data_site
bitprobavg: bit02 bit03 bit04 bit06 bit07 bit08 bit09 bit11 bit12 bit14 bit16 bit17 bit18 bit21 bit23 bit24 bit26 bit27 bit28 bit30 bit32 bit33 bit34 bit35 bit36 bit37 bit38 bit39 bit40 bit41 bit42

```{r}
social_problem_measures = inner_join(valuable_dataset, model_w2, 
                 by = c("child_id", "par_id")) %>%
  inner_join(model_w6, by = c("child_id", "par_id")) %>%
  select(n_devices, tv_exposure, digital_babysitting, daily_use,
         parenting_class_taken, data_site, 
         BITprobavg.x, BITprobavg.y, solo, passive, coop) %>% 
  mutate(different = BITprobavg.y - BITprobavg.x)

social_problem_measures %>% 
  ggplot(aes(x = data_site,
             y = different)) +
  geom_boxplot()
#No difference between the spread of data on both site,

social_problem_measures %>% 
  ggplot(aes(x = n_devices,
             y = different)) +
  geom_point() +
  geom_smooth()
#the number of devices makes no difference between on the change in development of social problems

social_problem_measures %>% 
  ggplot(aes(x = tv_exposure,
             y = different)) +
  geom_point() + 
  geom_smooth()
#tv exposure makes no difference between on the change in development of social problems

social_problem_measures %>% 
  ggplot(aes(x = digital_babysitting,
             y = different)) +
  geom_point() + 
  geom_smooth()
#digital babysitting makes no difference between on the change in development of social problems

social_problem_measures %>% 
  ggplot(aes(x = daily_use,
             y = different)) +
  geom_point() + 
  geom_smooth()
#daily use makes no difference between on the change in development of social problems
social_problem_measures %>% 
  ggplot(aes(x = solo,
             y = different)) +
  geom_point() + 
  geom_smooth()
#solo use makes no difference between on the change in development of social problems
social_problem_measures %>% 
  ggplot(aes(x = coop,
             y = different)) +
  geom_point() + 
  geom_smooth()
#coop use makes no difference between on the change in development of social problems
social_problem_measures %>% 
  ggplot(aes(x = passive,
             y = different)) +
  geom_point() + 
  geom_smooth()
#passive use makes no difference between on the change in development of social problems
count(social_problem_measures, different)

```



```{r}

social_competency_measures = inner_join(valuable_dataset, model_w2, 
                 by = c("child_id", "par_id")) %>%
  inner_join(model_w6, by = c("child_id", "par_id")) %>%
  select(n_devices, tv_exposure, digital_babysitting, daily_use,
         parenting_class_taken, data_site, 
         BITcompavg.x, BITcompavg.y, solo, passive, coop) %>% 
  mutate(different = BITcompavg.y - BITcompavg.x)

social_competency_measures %>% 
  ggplot(aes(x = data_site,
             y = different)) +
  geom_boxplot()
#No difference between the spread of data on both site,

social_competency_measures %>% 
  ggplot(aes(x = n_devices,
             y = different)) +
  geom_point() +
  geom_smooth()
#the number of devices makes no difference between on the change in development of social competency

social_competency_measures %>% 
  ggplot(aes(x = tv_exposure,
             y = different)) +
  geom_point() + 
  geom_smooth()
#tv exposure makes no difference between on the change in development of social competency

social_competency_measures %>% 
  ggplot(aes(x = digital_babysitting,
             y = different)) +
  geom_point() + 
  geom_smooth()
#digital babysitting makes no difference between on the change in development of social competency

social_competency_measures %>% 
  ggplot(aes(x = daily_use,
             y = different)) +
  geom_point() + 
  geom_smooth()
#daily use makes no difference between on the change in development of social competency
social_competency_measures %>% 
  ggplot(aes(x = solo,
             y = different)) +
  geom_point() + 
  geom_smooth()
#solo use makes no difference between on the change in development of social competency
social_competency_measures %>% 
  ggplot(aes(x = coop,
             y = different)) +
  geom_point() + 
  geom_smooth()
#coop use makes no difference between on the change in development of social competency
social_competency_measures %>% 
  ggplot(aes(x = passive,
             y = different)) +
  geom_point() + 
  geom_smooth()
#passive use makes no difference between on the change in development of social competency
```


# James

## preparing

- numeric:
  * w1: n_devices, tv_exposure, solo, passive, coop, mealtimes, behavior_management, positive_beliefs_media, educational_benefits, digital_babysitting, daily_use, auditory_comprehension_score, expressive_communication_score, total_score, household_income_numerical
  * w2: BITcompnic, BITcompts, BITcompavg, BITprobnic, BITprobts, BITprobavg
  * w6: BITcompnic, BITcompts, BITcompavg, BITprobnic, BITprobts, BITprobavg

- categorical:
  * w1: degree_cert_in_prog, parenting_class_taken, highest_degree_completed, years_school_complete, us_education, education_location, span_lang_form, father, data_site, par_ethnicity, par_us_born, par_language, chi_girl, birth_time, planned_preg, chi_ethnicity, chi_par_lang, relatives_lang, father, language, state_welfare, unemployment_insurance, food_stamp, wic, child_support, ssi_and_ssdi, adoption_assistance, utility_assistance, childcare_subsidy, vertan_benefit, medical_assistance, none, other, assistance, par_gen, household_others, marital_status, recieve_childcare, childcare_center, homebased_care, relative_care, other_care, par_gen, household_income_categorical, employment_status, enough_money_clothes, enough_money_food, enough_money_medical_care, bill_difficulty, father, speaking_english, reading_english, writing_english, understanding_english, english_level
  * w2: BITcomp_cut, BITprob_cut
  * w6: BITcomp_cut, BITprob_cut

## For loop

```{r}
w1_num <- list("n_devices" , "tv_exposure" , "solo" , "passive" , "coop" , "mealtimes" , "behavior_management" , "positive_beliefs_media" , "educational_benefits" , "digital_babysitting" , "daily_use" , "auditory_comprehension_score" , "expressive_communication_score" , "total_score" , "household_income_numerical")
w2_num <- list("BITcompnic_w2", "BITcompts_w2", "BITcompavg_w2", "BITprobnic_w2", "BITprobts_w2", "BITprobavg_w2")
w6_num <- list("BITcompnic_w6", "BITcompts_w6", "BITcompavg_w6", "BITprobnic_w6", "BITprobts_w6", "BITprobavg_w6")

w1_cat <- list("degree_cert_in_prog" , "parenting_class_taken" , "highest_degree_completed" , "years_school_complete" , "us_education" , "education_location" , "span_lang_form" , "father" , "data_site" , "par_ethnicity" , "par_us_born" , "par_language" , "chi_girl" , "birth_time" , "planned_preg" , "chi_ethnicity" , "chi_par_lang" , "relatives_lang" , "father" , "language" , "state_welfare" , "unemployment_insurance" , "food_stamp" , "wic" , "child_support" , "ssi_and_ssdi" , "adoption_assistance" , "utility_assistance" , "childcare_subsidy" , "vertan_benefit" , "medical_assistance" , "none" , "other" , "assistance" , "par_gen" , "household_others" , "marital_status" , "recieve_childcare" , "childcare_center" , "homebased_care" , "relative_care" , "other_care" , "par_gen" , "household_income_categorical" , "employment_status" , "enough_money_clothes" , "enough_money_food" , "enough_money_medical_care" , "bill_difficulty" , "father" , "speaking_english" , "reading_english" , "writing_english" , "understanding_english" , "english_level")
w2_cat <- list("BITcomp_cut_w2" , "BITprob_cut_w2")
w6_cat <- list("BITcomp_cut_w6" , "BITprob_cut_w6")
```
#### Merge all three datasets

```{r}
model_full <- full_join(model_w6, model_w2, by=c("par_id", "child_id"), suffix = c("_w6", "_w2")) %>% 
  full_join(valuable_dataset, by=c("par_id", "child_id"), suffix = c("_w62", "_w1"))
```


#### numeric for w2 and w6


##### point for w2 and w6
```{r}
for (i in w2_num){
  for (j in w6_num){
    plot <- ggplot(model_full, 
              aes_string(x = i, 
                         y = j))
    print(plot + geom_jitter())
    print(plot + geom_smooth())
  }
}
```
##### multiplot function
```{r}
multiplot = function(data, list_col, plot_type){
  list_plot <- list()
  counter = 0
  for (i in list_col){
    tmp <- ggplot(data, 
                  aes_string(x = i)) +
                  plot_type
    counter = counter + 1
    list_plot[[counter]] <- tmp
  }
  return(list_plot)
}
```

#### numeric for w1 and w2
```{r}
for (i in w1_num){
  for (j in w2_num){
    plot <- ggplot(model_full, 
              aes_string(x = i, 
                         y = j))
    print(plot + geom_point())
  }
}
```


##### compare w2 and w6


```{r}
hist1 <- multiplot(model_full, w2_num, geom_histogram())
hist2 <- multiplot(model_full, w6_num, geom_histogram())

for (i in 1:length(w2_num)) {
  print(hist1[i])
  print(hist2[i])
}

```

#### something


# seperator
