---
title: "Exploratory Data Analysis"
author: "Nicholas Noel"
date: '2022-06-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)

```



```{r}
# total na values per column
colSums(is.na(media_tech_cleaned))

# percentage na values per column
colMeans(is.na(media_tech_cleaned))
```

```{r}
# visualizing na values
library(visdat)
vis_miss(media_tech_cleaned)
```

```{r}
# correlation between average score data
library(ggcorrplot)
average_scores <- media_tech_cleaned %>% 
  select(!starts_with("q"), -child_id, -par_id)

correlation <- cor(average_scores, use = "complete.obs")

correlation
```

```{r}
# visualizing correlation
ggcorrplot(correlation,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white")

```

```{r}
valuable_dataset %>% 
         ggplot(aes(x = positive_beliefs_media,
             y = household_income_numerical,
             fill = parenting_class_taken)) +
  geom_boxplot()
```

```{r}
ggplot(data = parent_demographic, aes( 
  x= par_ethnicity)) +
geom_bar()
parent_demographic %>% 
  ggplot(aes(x = chi_par_lang)) + 
  geom_bar()
#most parents speak either english or spanish to their children
parent_demographic %>% 
  ggplot(aes(x = par_language)) + 
  geom_bar()
#majority parents speak english/spanish
parent_demographic %>% 
  ggplot(aes(x = par_us_born)) + 
  geom_bar()
#Slightly more than half of the parents were born outside of the U.S.
```

```{r}
  ggplot(data= valuable_dataset, aes(x=par_ethnicity, 
             y= total_score,
             fill = par_ethnicity)) +
  geom_boxplot(alpha = 0.3) +
  labs(x= "Parent Ethnicity",
       y= "Total Score") + 
  theme(panel.grid.major = element_blank(), 
                 panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text.x=element_blank(),
        legend.title = element_text(colour = "steelblue", face = "bold.italic",)) +
  ggtitle("Spread of ACS")
  
valuable_dataset %>% 
  ggplot(aes(x = par_us_born,
             y = auditory_comprehension_score)) + 
  geom_boxplot() +
  labs(x = "Parent Born in U.S.",
       y= "Auditory Comprehension Score") +
  theme_minimal()

valuable_dataset %>% 
  ggplot(aes(x = chi_girl,
             y = total_score)) + 
  geom_boxplot() +
  labs(x = "Was The form in spanish?",
       y= "Auditory Comprehension Score") +
  theme_minimal()

valuable_dataset %>% 
  mutate(years_school_complete = as.character(years_school_complete)) %>% 
  ggplot(aes(x = years_school_complete,
             y = total_score)) + 
  geom_boxplot()
   
valuable_dataset %>% 
  mutate(daily_use = as.numeric(daily_use)) %>% 
  ggplot(aes(x = solo, 
             y = daily_use)) +
  geom_point()

valuable_dataset %>%
  ggplot(aes(x = total_score,
             y= daily_use)) +
  geom_point()

valuable_dataset %>% 
  ggplot(aes(x = household_income_numerical,
             y = daily_use)) +
  geom_point()

valuable_dataset %>% 
  ggplot(aes(x = positive_beliefs_media,
             y = total_score)) + 
  geom_point()

valuable_dataset %>% 
  ggplot(aes(x = passive,
             y = daily_use)) + 
  geom_point()

valuable_dataset %>% 
  ggplot(aes(x = q7a,
             y = daily_use)) +
  geom_boxplot()

valuable_dataset %>% 
  ggplot(aes(x = tv_exposure,
             y = daily_use)) +
  geom_point()

valuable_dataset %>% 
  ggplot(aes(x = coop,
             y = total_score)) +
  geom_point()

valuable_dataset %>% 
  ggplot(aes(x = coop,
             y = daily_use)) +
  geom_point()

valuable_dataset %>% 
  ggplot(aes(x = n_devices,
             y = positive_beliefs_media)) + 
  geom_point()

#q8: do you limit how much time the children use 
valuable_dataset %>% 
  ggplot(aes(x =  positive_beliefs_media,
             y = highest_degree_completed,
             fill = parenting_class_taken)) +
  geom_boxplot()

valuable_dataset %>% 
  ggplot(aes(y = household_income_numerical,
             x = highest_degree_completed,
             fill = highest_degree_completed)) +
  geom_boxplot()

valuable_dataset %>% 
  ggplot(aes(x = positive_beliefs_media,
             y = daily_use,
             fill = positive_beliefs_media)) +
  geom_point()

```

```{r}
model_score_demographic = full_join(model_score, parent_demographic, by=c("child_id", "par_id"))
```

```{r}
model_score_demographic %>% 
  glimpse()
```

```{r}
model_score_demographic %>% 
  ggplot(aes(x = chi_ethnicity,
             y = total_score))+
  geom_col()
```

---

According to Dr. Reich's email here are some preliminary exploratory data analysis here are some relationships that may be of interest:

* Are the English scores of the parent related to the standardized expressive or auditory comprehension scores?
  + model_score
  + parent_english_fluency
  
* are solo/passive/coop infant media measurements related to parent's education attainment?
  + media_tech_cleaned
  + parent_education
  
---

