---
title: "Exploratory Data Analysis"
author: "Nicholas Noel"
date: '2022-06-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)
demographic_background <- read_dta("../data/wave-1-(9-mo)/1_DEM_w1.dta")
media_tech <- read_dta("../data/wave-1-(9-mo)/10_MT_w1.dta")
overall_background <- read_dta("../data/wave-1-(9-mo)/2_BCK_w1.dta")
scores_w1 <- read_dta("../data/wave-1-(9-mo)/26_PLS_w1.dta")
w1_codebook <- read_excel("../data/wave-1-(9-mo)/BB2_w1_codebook.xls.xlsx")

wave_2 <- read_dta("../data/wave-2-(12-mo)/31_BIT_w2.dta")
#wave_2_codebook <- read_excel("../data/wave-2-(12-mo)/BB2_w2_codebook.xls.xlsx")

#wave_6 <- read_dta("../data/wave-6-(24-mo)/BB2_W6_BIT.dta")
#wave_6_codebook <- read_excel("../data/wave-6-(24-mo)/BB2_w6_BITSE_codebook.xls.xlsx")
```

# Aubree's code

```{r}
```

# Chandra's code

```{r}
```

# Deborah's code

```{r}
```

# James' code

## clean data

```{r}
scores_w1 <- clean_names(scores_w1)
glimpse(scores_w1)
```
```{r}
scores_w1 <-  scores_w1 %>% 
  mutate(pargen = as.factor(case_when(
          pargen == 1 ~ "male",
          pargen == 0 ~ "female"
        )),
        language_26_PLS_w1 = as.factor(case_when(
          language_26_pls_w1 == 0 ~ "english",
          language_26_pls_w1 == 1 ~ "spanish"
        )),
        site = as.factor(case_when(
          site == 1 ~ "UMD",
          site == 2 ~ "UCI"
        )))
```

### Variable meaning

|variable name| description|
|-------------|------------|
|childid| Child ID|
|parid| Parent ID|
|wave| wave index|
|version_26_PLS_w1| version of this form? (we definitely dont need this)|
|pargen| Parent gender|
|site | no use|
|language_26_PLS_w1| From language|
|plsacraw| Auditory Comprehension raw score|
|plsecraw| Expressive Communication raw score|
|plsraw| Total raw score (AC raw  + EC raw)|
|plsacss| Auditory Comprehension standard score|
|plsacpr| Auditory Comprehension percentile rank|
|plsecss| Expressive Communication standard score|
|plsecpr| Expressive Communication percentile rank|
|plsss| Total Standard Score|
|plspr| Total score percentile rank|


# Nick's code

```{r}
print("Don't touch my code chunk or I'll fight you - Nick")

```