---
title: "anova-aubree"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)
```

```{r}
model_w2 <- readRDS(file="../data/model_w2.dta")
model_w6 <- readRDS(file="../data/model_w6.dta")
valuable_dataset <- readRDS(file="../data/valuable_dataset.dta")
```

```{r}
PLS_data <- readRDS(file="../data/PLS_data.dta")
BIT_data <- readRDS(file="../data/BIT_data.dta")
media_data <- readRDS(file="../data/media_data.dta")
demography <- readRDS(file="../data/demography.dta")
mt_w6_cleaned <- readRDS(file = "../data/media_wave_6.dta")
PLS_w6 <- readRDS(file = "../data/PLS_w6.dta")
```

### Creating tables

Thoughts/Ideas:
* explore an ANOVA model to see if the hypothesized predictors that have factors are actually significant
* definitely check out the most efficient linear model according to Aubree's ML code that optimized for certain parameters
* ANCOVA model is mixes linear regression with anova, this ultimately may be a good idea to implement since MEDIA, PLS, BITSEA, Income are quantitative (numerical) and Ethnicity, Education are qualitative (categorical)

##### creating wave6 data for linear models

Here I've just started by creating a complete dataset for wave 6 for 3 datasets:
1. media
2. BITSEA
3. PLS

```{r}
#creating wave 6 dataset complete with 
wave6 <- inner_join(mt_w6_cleaned, model_w6, key = c(par_id, child_id))
wave6 <- inner_join(wave6, PLS_w6, key = c(par_id, child_id) )

wave6 <- wave6 %>% 
  filter(wave == 6) %>% 
  glimpse()

#wave6 <- inner_join(wave6, valuable_dataset, key = c(par_id, child_id) )
wave6 %>% 
  glimpse()
```

##### creating table for ANOVA model

Here I added education to try and create an ANOVA model to see if we get a better quality model.

```{r}
#education doesn't change across waves (assumption)
ed <- valuable_dataset %>% 
  select(highest_degree_completed, child_id, par_id)

wave6 <- inner_join(wave6, ed, key = c(par_id, child_id) )

wave6 %>% 
  glimpse()

#here I'm getting rid of NA values in the education factor
wave6 <- wave6 %>% 
  filter(!is.na(highest_degree_completed)) %>% 
  glimpse()

```

AH YES CLARITY:

```{r}
# wave 1 media and pls 
pls_media_w1 <- valuable_dataset %>% 
  filter(wave.y.y == 1) %>% 
  mutate(wave = as.factor(wave.y.y)) %>% 
  select(wave, child_id, par_id, total_score, daily_use) 

# wave 6 media and pls 
pls_media_w6 <- wave6 %>% 
  select(wave, child_id, par_id, total_score, daily_use)

#this may have done it, just joining with child and parent ids
anova_table <- full_join(pls_media_w1, pls_media_w6 ,key = c(child_id, par_id))

#now there are missing value codes, NAs, and wave 4 data (for some reason??), I need to get rid of:
anova_table <- anova_table %>% 
  na.omit() %>% 
  filter( 
    total_score != -111,
    total_score != -222,
    total_score != -333,
    total_score != -444,
    total_score != -555,
    total_score != -666,
    total_score != -777,
    total_score != -888,
    total_score != -999,
    wave != 4
    )
#this categorizes daily_use as high-med-low, as an extra factor variable
anova_table <- anova_table %>% 
mutate(
  daily_use_cat = case_when(
    daily_use <= 0.4 ~ "LOW",
    daily_use > 0.4 ~ "HIGH")
      )
## anova_table <- anova_table %>% 
#mutate(
 # daily_use_cat = case_when(
 #   daily_use <= 0.25 ~ "LOW",
  #  daily_use < 0.5 ~ "MED",
  #  daily_use >= 0.5 ~ "HIGH")
   #   )


anova_table <- anova_table %>% 
  mutate(daily_use_cat = as.factor(daily_use_cat))

#now we need the same number of child ids for wave 6 and wave 1
anova_table %>% 
  glimpse()


```

BOX PLOTS
```{r}
anova_table %>% 
  ggplot(aes(x = daily_use_cat, 
         y = total_score,
         color = daily_use_cat)) + 
geom_boxplot() + 
  geom_jitter() + 
  facet_grid(~ wave)
```

## Deborah's eda file has tests to show staticlly what we see in the graphs. 

```{r}
bit <- readRDS("../data/BIT_long_mother.dta")
bit$wave[bit$wave == 2] <- 1

# bit$wave[bit$wave == 5] <- 4
```


```{r}
bit_and_anova_table <- full_join(bit, anova_table, by = c("child_id", "par_id", "wave"))

bit_and_anova_table <- 
  bit_and_anova_table %>% 
select("par_id", "child_id",  "wave", "total_score", "daily_use_cat", "BITprobavg")

bit_and_anova_table <- bit_and_anova_table %>% 
  filter(wave != 5) %>% 
  na.omit()

bit_and_anova_table <- bit_and_anova_table %>% 
mutate(
  BITprobavg_cat = case_when(
    BITprobavg <= 0.3 ~ "LOW",
    BITprobavg < 0.6 ~ "MED",
    BITprobavg >= 0.6 ~ "HIGH")
      )

bit_and_anova_table <- bit_and_anova_table %>% 
mutate(
  BITprobavg_cat = case_when(
    BITprobavg <= 0.3 ~ "LOW",
    BITprobavg < 0.6 ~ "MED",
    BITprobavg >= 0.6 ~ "HIGH")
      )

#bit_and_anova_table <- bit_and_anova_table %>% 
#mutate(
#  total_score_cat = case_when(
 #   total_score <= 97 ~ "LOWts",
#    total_score > 97 ~ "HIGHts")
 #     )


bit_and_anova_table <- bit_and_anova_table %>% 
mutate(
  total_score_cat = case_when(
    total_score <= 80 ~ "LOW",
    total_score < 110 ~ "MED",
    total_score >= 110 ~ "HIGH")
      )

hist(bit_and_anova_table$)


anova_2 <- aov(BITprobavg ~ total_score_cat + daily_use_cat + total_score_cat:daily_use_cat, data = bit_and_anova_table)
summary(anova_2)
```

```{r}
tukey.test <- TukeyHSD(anova_2)
plot(tukey.test)

TukeyHSD(anova_2)
```



