```{r}
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)
library(ggcorrplot)
```

### Loading the Data Table

##### One Way Table
```{r}
model_w2 <- readRDS(file="../data/model_w2.dta")
model_w6 <- readRDS(file="../data/model_w6.dta")
valuable_dataset <- readRDS(file="../data/valuable_dataset.dta")
```

```{r}
PLS_data <- readRDS(file="../data/PLS_data.dta")
BIT_data <- readRDS(file="../data/BIT_data.dta")
media_data <- readRDS(file="../data/media_data.dta")
demography <- readRDS(file="../data/demography.dta")
```

```{r}
#creating wave 6 dataset complete with 
wave6 <- inner_join(mt_w6_cleaned, model_w6, key = c(par_id, child_id))
wave6 <- inner_join(wave6, PLS_w6, key = c(par_id, child_id) )

wave6 <- wave6 %>% 
  filter(wave == 6)

```

```{r}
#education doesn't change across waves (assumption)
ed <- valuable_dataset %>% 
  select(highest_degree_completed, child_id, par_id)

wave6 <- inner_join(wave6, ed, key = c(par_id, child_id) )

#here I'm getting rid of NA values in the education factor
wave6 <- wave6 %>% 
  filter(!is.na(highest_degree_completed))
```

```{r}
# wave 1 media and pls 
pls_media_w1 <- valuable_dataset %>% 
  filter(wave.y.y == 1 ) %>% 
  mutate(wave = as.factor(wave.y.y),
         pargen = as.character(par_gen.x)) %>% 
  select(wave, child_id, par_id, pargen, total_score, daily_use) 

# wave 6 media and pls 
pls_media_w6 <- wave6 %>% 
  select(wave, child_id, par_id, pargen, total_score, daily_use)

#this may have done it, just joining with child and parent ids
anova_table <- full_join(pls_media_w1, pls_media_w6 ,key = c(child_id, par_id))
#anova_table <- full_join(anova_table, pls_media_w4,key = c(child_id, par_id))

#now there are missing value codes, NAs, and wave 4 data (for some reason??), I need to get rid of:
anova_table <- anova_table %>% 
  na.omit() %>% 
  filter( 
    total_score != -111,
    total_score != -222,
    total_score != -333,
    total_score != -444,
    total_score != -555,
    total_score != -666,
    total_score != -777,
    total_score != -888,
    total_score != -999,
    )
#this categorizes daily_use as high-med-low, as an extra factor variable
anova_table <- anova_table %>% 
mutate(
  daily_use_cat = case_when(
    daily_use == 0 ~ "recommended",
    daily_use > 0 ~ "NOT recommended"
                           )
      )
#converting daily_use_cat into a factor and setting the right order
anova_table <- anova_table %>% 
  mutate(daily_use_cat = as.factor(daily_use_cat),
         daily_use_cat = fct_relevel(
           daily_use_cat, 
           "LOW", 
           "MED", 
           "HIGH"
           )
         )
#Just mothers media observations
anova_table <- anova_table %>% 
  filter(pargen == 0)

#trying to add BITprobavg

#solo, passive, coup mealtimes


#now we need the same number of child ids for wave 6 and wave 1 - we've paused about this
#anova_table %>% 
#  glimpse()
```


##### Table for spaghetti plot

```{r}
# table for spaghetti plot

anova_table <- anova_table %>% 
  group_by(child_id) %>% 
  filter(n() == 2) %>%
  distinct() %>% 
  glimpse()

# IN PROGRESS
#anova_table <- anova_table %>% 
#mutate(
#  pls_change = case_when(
#    total_score <= 0.25 ~ "LOW",
#    daily_use < 0.5 ~ "MED",
#    daily_use >= 0.5 ~ "HIGH")
#      )

pls_diff_w1w6 <- full_join(PLS_w1, PLS_w6, by = c("child_id", "par_id"))

pls_diff_w1w6 <- pls_diff_w1w6 %>% 
  select(wave.y, 
         wave.x, 
         total_score.x, 
         total_score.y, 
         father, 
         child_id, 
         par_id) %>% 
  filter(father == FALSE,
         total_score.y > 0,
         total_score.x > 0) %>% 
  mutate(
    pls_change = as.numeric(total_score.x - total_score.y),
    pls_change_cat = case_when(
    pls_change == 0 ~ "constant",
    pls_change < 0 ~ "decreasing",
    pls_change > 0 ~ "increasing"
    )
      )

anova_table <- left_join(anova_table, pls_diff_w1w6, key = c("child_id", "par_id"))

#finalized selection of variables
anova_table <- anova_table %>% 
  select(child_id, par_id, wave, pls_change, pls_change_cat, father, total_score, daily_use, daily_use_cat) %>%
  na.omit() 
```


##### Table for change pls

```{r}
anova_table_no_double <- anova_table %>% 
  filter(wave == 6)
```

##### Two Way Table

```{r}
bit <- readRDS("../data/BIT_long_mother.dta")
bit$wave[bit$wave == 2] <- 1

# bit$wave[bit$wave == 5] <- 4

bit_and_anova_table <- full_join(bit, anova_table, by = c("child_id", "par_id", "wave"))

bit_and_anova_table <- 
  bit_and_anova_table %>% 
select("par_id", "child_id",  "wave", "total_score", "daily_use_cat", "BITprobavg")

bit_and_anova_table <- bit_and_anova_table %>% 
  filter(wave != 5) %>% 
  na.omit()

bit_and_anova_table <- bit_and_anova_table %>% 
mutate(
  BITprobavg_cat = case_when(
    BITprobavg <= 0.3 ~ "LOW",
    BITprobavg < 0.6 ~ "MED",
    BITprobavg >= 0.6 ~ "HIGH")
      )

bit_and_anova_table <- bit_and_anova_table %>% 
mutate(
  BITprobavg_cat = case_when(
    BITprobavg <= 0.3 ~ "LOW",
    BITprobavg < 0.6 ~ "MED",
    BITprobavg >= 0.6 ~ "HIGH")
      )

bit_and_anova_table <- bit_and_anova_table %>% 
mutate(
  total_score_cat = case_when(
    total_score <= 80 ~ "LOW_ts",
    total_score < 110 ~ "MED_ts",
    total_score >= 110 ~ "HIGH_ts")
      )
```

---
Data Observations:
* the daily_use measurement for a single child is different depending on the parent asked
* a single child is counted twice, since there are both mother and fathers in these data sets
  + we should likely include parent gender, gender is included
* PLS score is unique to each child, it was not assessed through each parent so it shouldn't vary by mother or father
  
### EDA

##### Histogram of infant daily media usage in wave 1 and wave 6:

```{r}
ggplot(data = anova_table,
       aes(x = daily_use)) +
  geom_histogram(fill = "blue") +
  ggtitle('Distribution of media usage for wave 1 and wave 6') +
  facet_grid(~wave) +
  theme_grey()
```
Observations:

Wave 1 and wave 6 are very different from one another potentially because wave 1 media habits weren't collect as well as possible, (skip questions were implemented). What's nice is that wave 6 seems like it's approximately normally distributed, meanwhile wave 1 could be chi-squared distributed or  at least right skewed. So obviously the means and medians between these two waves are different.


##### Boxplots of PLS scores and Infant Media Usage by Category

```{r}
ggplot(anova_table, aes(x = daily_use_cat, y = total_score, color = daily_use_cat)) +
  geom_violin(trim = FALSE) +
  geom_boxplot(width = 0.4) +
  #geom_jitter() +
  facet_grid(~wave)
```
##### Boxplots of CHANGE in PLS scores and Infant Media Usage by Category

```{r}
ggplot(anova_table_no_double, aes(x = daily_use_cat, y = pls_change, color = daily_use_cat)) +
  geom_violin(trim = FALSE) +
  geom_boxplot(width = 0.3) 
  #geom_jitter() +
  #facet_grid(~wave)
```
This graph implies that children not following recommended media use have an average positive change in pls scores (increasing pls scores), meanwhile infants who are following recommended media use have an average negative change in pls scores (decreasing).

To avoid double counting, it only oncludes wave 6.
##### Scatterplot of PLS scores and Infant Media Use 
```{r}
ggplot(anova_table, aes(x = daily_use, y = total_score, color = daily_use_cat)) +
  geom_point() +
  facet_grid(~wave) +
  geom_smooth(method=lm)


#ggplot(anova_table, aes(x = total_score, y = daily_use)) +
#geom_point(size=2, shape=23)
```
##### Histogram of PLS scores filled by Media Usage

```{r}
ggplot(anova_table, aes(x=total_score, fill=daily_use_cat)) + 
  geom_histogram(color="darkgreen") +
  facet_grid(~wave)

```

##### Spaghetti Plots of PLS scores
```{r}
interaction.plot(
x.factor = anova_table$wave,
trace.factor = anova_table$child_id,
response = anova_table$total_score,
type = "o",
xlab = "Waves (9mo and 24mo)",
ylab = "PLS Scores",
lty = 1,
pch = 19,
legend = FALSE,
main = "Spaghetti Plot of PLS Scores"
)
```

```{r}
anova_table%>%
  ggplot() +
  aes(x = wave, y = total_score, group = child_id, color = daily_use_cat) +
  geom_point() +
  geom_line() +
  xlab("Waves (9mo and 24mo)") +
  ylab("PLS Scores") +
  ggtitle("Spaghetti Plot of PLS Scores") +
  labs(color = "total_s") +
  labs(color = "Infant Media Use") +
  theme_bw() +
  theme(
  text = element_text(family = "Times"),
  plot.title = element_text(hjust = 0.5)
)

```

```{r}
anova_table%>%
  ggplot() +
  aes(x = wave, y = daily_use, group = child_id, color = daily_use_cat) +
  geom_point() +
  geom_line() +
  xlab("Waves (9mo and 24mo)") +
  ylab("Daily Use of Media") +
  ggtitle("Spaghetti Plot of Daily Use of Media Wave 1 and Wave 6") +
  labs(color = "total_s") +
  labs(color = "Infant Media Use") +
  theme_bw() +
  theme(
  text = element_text(family = "Times"),
  plot.title = element_text(hjust = 0.5)
)

```

Observations:

PLS scores are not normally distributed, however generally there's the least amount of counts for infants who had higher media exposure. It's worth noting that the mean for PLS scores for both waves looks a bit less than 100. Wave one is right skewed, potentially because of a few outliers, meanwhile wave 6 is well clustered.


##### Histograms of Most Important Variables
```{r}
ggplot(anova_table, aes(x=total_score, fill = daily_use_cat)) + 
  geom_histogram( bins = 30) +
  labs(title  = "Distribution of Infant PLS Scores for Waves 1 and 6", x ="Infant PLS Scores") + 
  facet_grid(~wave)
#color ="white", fill = "pink",
```

Observations:
PLS scores in both waves are approx normal.

```{r}
bit_and_anova_table %>% 
ggplot(aes(x = BITprobavg)) + 
  geom_histogram(color ="white", fill = "darkorange", 
                 bins = 30) + 
  labs(title  = "Distribution of Infant BITSEA scores for Waves 1 and 6", x = "Infant BITSEA scores") + 
  facet_grid(~wave)

```

Observations:
BITSEA scores in both waves MAY be approx normal.

```{r}
anova_table %>% 
ggplot(aes(x = daily_use)) + 
  geom_histogram(color ="white", fill = "lightblue", 
                 bins = 15) + 
  labs(title  = "Distribution of Infant Media Usage for Waves 1 and 6", x = "Infant Daily Media Use") + 
  facet_grid(~wave)

```

Observations:
Media Usage in wave 6 is approx normal, n wave 1 it is not approx normal, more chi-squared.


### 1-Way Anova Models:

__ANOVA takes into account variability within groups and between groups, by comparing means among groups.__

_Assumptions are consistent regardless of whether ANOVA is balanced or not:_
1. responses follow a normal distribution 
  * PLS scores histograms look approx. normal, but if take the sample means of pls scores in each media category and bootstrap then according to CLT we should be able to say that the sample means follow a approx normal distribution (check out ppt for wk2 for origial histogram of pls scores (not means of scores))

2. Observations are independent within and between groups
  * questionable as media usage and receptive and expressive communication skills are likely dependent (or are they? potential HYPOTHESIS TEEESTT BBBAABBYYY) 

3. errors/residuals are normally distributed with a constant variance, expectation 0
  * totally unknown
  
##### PLS scores = Media rec/not rec
```{r}
pls_media <- aov(total_score ~ daily_use_cat, anova_table)

pls_media %>% 
  summary()
```


##### change in PLS = Media rec/not rec

```{r}
pls_change_media <- aov(pls_change ~ daily_use_cat, anova_table_no_double)

pls_change_media %>% 
  summary()
```
Why is this significant?

##### PLS = Media 
```{r}
pls_media <- aov(total_score ~ daily_use_cat, anova_table)

summary(pls_media)
```
##### PLS = Media 

```{r}
aov_model <- aov(total_score ~ daily_use_cat, anova_table)
summary(aov_model)
```

### 2-Way Anova Models:

##### BITSEA = PLS + Media 
```{r}
anova_2 <- aov(BITprobavg ~ total_score_cat + daily_use_cat, data = bit_and_anova_table)
summary(anova_2)
```


##### Tukey Test for Two Way Anova
```{r}
#https://rpubs.com/aaronsc32/post-hoc-analysis-tukey

tukey.test <- TukeyHSD(anova_2)
plot(tukey.test)


TukeyHSD(anova_2)
```
##### PLS = Media + parent Gender

```{r}
#aov_model <- aov(total_score ~ daily_use_cat + pargen + pargen:daily_use_cat , anova_table)

#(aov_model)
```
Interpretation:

Parent gender is not a significant covariate in this two-way anova model. Not a significant different in PLS scores based on parent gender.

### Hypothesis Testing

##### Contingency Table of CHANGE in PLS and daily use Rec/Not Rec

```{r}
cont_table_change_pls_media <- table(anova_table_no_double$pls_change_cat, anova_table_no_double$daily_use_cat)
cont_table_change_pls_media
```

##### Chi-Squared Test of Indepdendence

H0: pls_change and daily_use are independent (unrelated)
H1: PLs_change and daily_use are dependent (related)

```{r}
chisq.test(anova_table_no_double$pls_change_cat, anova_table_no_double$daily_use_cat)
```
Not enough evidence to reject null hypothesis when we take into account double counting
NO EVIDENCE = NOT DEPENDENT = 

FAIL TO REJECT NULL HYPOTHESIS, HENCE THERE IS NOT ENOUGH EVIDENCE TO SAY THAT THE VARIABLES ARE DEPENDENT

AKA media categories and change in pls scores are independent.






