#Chandra go to line 100 and thats where I start the cross lagged analysis
```{r}
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)
```


```{r}


pls_wide_mother <- readRDS(file="../data/PLS_wide_mother.dta")
pls_wide_father <- readRDS(file="../data/PLS_wide_father.dta")
pls_long <- readRDS(file="../data/PLS_long_mother.dta")
pls_long_father <- readRDS(file="../data/PLS_long_father.dta")

pls_wide <- full_join(pls_wide_mother, pls_wide_father)
media_wide <- readRDS(file="../data/media_wide.dta")

media_pls <- inner_join(media_wide, pls_wide, by = c("child_id", "par_id")) %>% filter(total_score.1 >0, total_score.4 > 0, total_score.6 >0)

library(readxl)


PLS_W1 <- read_dta("../data/wave-1-(9-mo)/26_PLS_w1.dta")
View(X26_PLS_w1)


PLS_w4 <- read_excel("../data/wave-4-(18-mo)/PLS_W4_Final.xlsx", sheet = "PLS_ALL_W4")
PLS_w6 <- read_excel("../data/wave-6-(24-mo)/PLS_W6.xlsx",sheet = "PLS_ALL_W6")


```


# clean w6 pls
```{r}
PLS_w6 <- clean_names(PLS_w6)
glimpse(PLS_w6)
```

```{r}
PLS_w6 <-  PLS_w6 %>% 
  mutate(child_id = as.double(childid),
         par_id = as.double(parid),
        language= as.factor(case_when(
          language == 0 ~ "english",
          language == 1 ~ "spanish")))
```


```{r}
PLS_w6 <- PLS_w6 %>%
  select(child_id, par_id, language, auditory_comprehension_score = plsacss, expressive_communication_score = plsecss, total_score = plsss, percentile_rank = plspr, auditory_comprehension_percentile = plsacpr, expressive_communication_percentile = plsecpr)
```

# clean w4 pls

```{r}
PLS_W4 <- clean_names(PLS_w4)
```

```{r}
PLS_W4 <-  PLS_W4 %>% 
  select(child_id = childid, par_id = parid, language,
         auditory_comprehension_score = plsacss,
         expressive_communication_score = plsecss,
         total_score = plsss, percentile_rank = plspr,
         auditory_comprehension_percentile = plsacpr,
         expressive_communication_percentile = plsecpr)
```

```{r}
PLS_W1 <- clean_names(PLS_W1) 
PLS_W1 <- PLS_W1 %>% 
  select(child_id = childid, par_id = parid, 
         auditory_comprehension_score = plsacss,
         expressive_communication_score = plsecss,
         total_score = plsss, percentile_rank = plspr,
         auditory_comprehension_percentile = plsacpr,
         expressive_communication_percentile = plsecpr)
  
```

```{r}
pls_total <-inner_join(PLS_W1, PLS_W4, by = c("child_id", "par_id"))

pls_all <-inner_join(pls_total, PLS_w6, by = c("child_id", "par_id"))

glimpse(pls_all)
```
#this combines the pls scores across waves
```{r}
pls_all <- pls_all %>% 
  filter(percentile_rank.x >0,
         percentile_rank >0,
         percentile_rank.y >0) %>% 
    mutate(child_id = as.character(child_id),
           par_id = as.character(par_id))
```

```{r}
media_wide <- media_wide %>% 
  mutate(child_id = as.character(child_id))
glimpse(media_wide)
```


```{r}
media_pls <- inner_join(pls_all, media_wide, by = c("child_id", "par_id"))
```

# mealtime predicting auditory comprehension scores
```{r}
#x across waves
mod1 <- lm(mealtimes.4 ~ mealtimes.1, data = media_pls)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ mealtimes.4, data = media_pls)
summary(mod1)
#y across waves
mod1 <- lm(auditory_comprehension_percentile.y ~ auditory_comprehension_percentile.x, data = media_pls)
summary(mod1)
mod1 <- lm(auditory_comprehension_percentile ~ auditory_comprehension_percentile.y, data = media_pls)
summary(mod1)
#y ~x
mod1 <- lm(auditory_comprehension_percentile.y ~ mealtimes.1 + auditory_comprehension_percentile.x, data = media_pls)
summary(mod1)
mod1 <- lm(auditory_comprehension_percentile ~ mealtimes.4 + auditory_comprehension_percentile.y, data = media_pls)
summary(mod1)
#x ~ y
mod1 <- lm(mealtimes.4 ~ auditory_comprehension_percentile.x + mealtimes.1, data = media_pls)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ auditory_comprehension_percentile.y + mealtimes.4, data = media_pls)
summary(mod1)
```

# mealtime predicting expressive communication percentile 
```{r}
#x across waves
mod1 <- lm(mealtimes.4 ~ mealtimes.1, data = media_pls)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ mealtimes.4, data = media_pls)
summary(mod1)
#y across waves
mod1 <- lm(expressive_communication_percentile.y ~ expressive_communication_percentile.x, data = media_pls)
summary(mod1)
mod1 <- lm(expressive_communication_percentile ~ expressive_communication_percentile.y, data = media_pls)
summary(mod1)
#y ~x
mod1 <- lm(expressive_communication_percentile.y ~ mealtimes.1 + expressive_communication_percentile.x, data = media_pls)
summary(mod1)
mod1 <- lm(expressive_communication_percentile ~ mealtimes.4 + expressive_communication_percentile.y, data = media_pls)
summary(mod1)
#x ~ y
mod1 <- lm(mealtimes.4 ~ expressive_communication_percentile.x + mealtimes.1, data = media_pls)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ expressive_communication_percentile.y + mealtimes.4, data = media_pls)
summary(mod1)
```

#mealtimes predicting percentile rank 
```{r}
#x across waves
mod1 <- lm(mealtimes.4 ~ mealtimes.1, data = media_pls)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ mealtimes.4, data = media_pls)
summary(mod1)
#y across waves
mod1 <- lm(percentile_rank.y ~ percentile_rank.x, data = media_pls)
summary(mod1)
mod1 <- lm(percentile_rank ~ percentile_rank.y, data = media_pls)
summary(mod1)
#y ~x
mod1 <- lm(percentile_rank.y ~ mealtimes.1 + percentile_rank.x, data = media_pls)
summary(mod1)
mod1 <- lm(percentile_rank ~ mealtimes.4 + percentile_rank.y, data = media_pls)
summary(mod1)
#x ~ y
mod1 <- lm(mealtimes.4 ~ percentile_rank.x + mealtimes.1, data = media_pls)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ percentile_rank.y + mealtimes.4, data = media_pls)
summary(mod1)
```

Time to get wild!!
```{r}
intervention <- read_xlsx("../data/UMD_UCI Condition_7.20.22.xlsx") %>% 
  mutate(child_id = as.character(ChildID))
media_pls <- full_join(media_pls, intervention, by = c("child_id"))
```

#mealtimes predicting percentile rank 
```{r}
media_pls_both <- media_pls %>% 
  filter(par_id >25000)
#x across waves
mod1 <- lm(mealtimes.4 ~ mealtimes.1, data = media_pls_both)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ mealtimes.4, data = media_pls_both)
summary(mod1)
#y across waves
mod1 <- lm(percentile_rank.y ~ percentile_rank.x, data = media_pls_both)
summary(mod1)
mod1 <- lm(percentile_rank ~ percentile_rank.y, data = media_pls_both)
summary(mod1)
#y ~x
mod1 <- lm(percentile_rank.y ~ mealtimes.1 + percentile_rank.x, data = media_pls_both)
summary(mod1)
mod1 <- lm(percentile_rank ~ mealtimes.4 + percentile_rank.y, data = media_pls_both)
summary(mod1)
#x ~ y
mod1 <- lm(mealtimes.4 ~ percentile_rank.x + mealtimes.1, data = media_pls_both)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ percentile_rank.y + mealtimes.4, data = media_pls_both)
summary(mod1)
```

#mealtimes predicting ec rank 
```{r}
media_pls_both <- media_pls %>% 
  filter(par_id >25000)
#x across waves
mod1 <- lm(mealtimes.4 ~ mealtimes.1, data = media_pls_both)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ mealtimes.4, data = media_pls_both)
summary(mod1)
#y across waves
mod1 <- lm(expressive_communication_percentile.y ~ expressive_communication_percentile.x, data = media_pls_both)
summary(mod1)
mod1 <- lm(expressive_communication_percentile ~ expressive_communication_percentile.y, data = media_pls_both)
summary(mod1)
#y ~x
mod1 <- lm(expressive_communication_percentile.y ~ mealtimes.1 + expressive_communication_percentile.x, data = media_pls_both)
summary(mod1)
mod1 <- lm(expressive_communication_percentile ~ mealtimes.4 + expressive_communication_percentile.y, data = media_pls_both)
summary(mod1)
#x ~ y
mod1 <- lm(mealtimes.4 ~ expressive_communication_percentile.x + mealtimes.1, data = media_pls_both)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ expressive_communication_percentile.y + mealtimes.4, data = media_pls_both)
summary(mod1)
```

#mealtimes predicting AC rank 
```{r}
media_pls_both <- media_pls %>% 
  filter(par_id >25000)
#x across waves
mod1 <- lm(mealtimes.4 ~ mealtimes.1, data = media_pls_both)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ mealtimes.4, data = media_pls_both)
summary(mod1)
#y across waves
mod1 <- lm(auditory_comprehension_percentile.y ~ auditory_comprehension_percentile.x, data = media_pls_both)
summary(mod1)
mod1 <- lm(auditory_comprehension_percentile ~ auditory_comprehension_percentile.y, data = media_pls_both)
summary(mod1)
#y ~x
mod1 <- lm(auditory_comprehension_percentile.y ~ mealtimes.1 + auditory_comprehension_percentile.x, data = media_pls_both)
summary(mod1)
mod1 <- lm(auditory_comprehension_percentile ~ mealtimes.4 + auditory_comprehension_percentile.y, data = media_pls_both)
summary(mod1)
#x ~ y
mod1 <- lm(mealtimes.4 ~ auditory_comprehension_percentile.x + mealtimes.1, data = media_pls_both)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ auditory_comprehension_percentile.y + mealtimes.4, data = media_pls_both)
summary(mod1)
```
