


I have all the necessary data sets but when I'm joining them using inner join the 
data set gets bigger which doesn't make sense considering what inner join is 
supposed to do. Besides that I have all the items you asked for but idk why like media_tech_all has 1056 observations:/

```{r}
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)
library(ggcorrplot)
library(here)
#install.packages("naniar")
library(naniar)
```
Inner join omits key observations that don't exist in both datasets, so it cuts down further on an already sparse dataframe! So I'm converting to full_join()

The datasets that we need include media and pls
```{r}
#211
media_tech_w1 <- read_dta("../data/wave-1-(9-mo)/10_MT_w1.dta") %>% 
  filter( pargen == 0) 
#165
media_tech_w4 <- read_dta("../data/wave-4-(18-mo)/BB2_W4-MT.dta") %>% 
  filter( pargen == 0)
#157
media_tech_w6 <- read_dta("../data/wave-6-(24-mo)/BB2_W6-MT.dta") %>% 
  filter( pargen == 0)
```

```{r}
#166
ignore <- full_join(media_tech_w1, media_tech_w4, by = c("childid"), suffix = c("_w1", "_w4"))

#145
media_tech_all <- full_join(ignore, media_tech_w6, by = c("childid"))
```

```{r}
media_tech_all <- media_tech_all %>% 
  select(childid, mt05c_w1, mt05c_w4, mt05c_w6 = mt05c, mt05d_w1, mt05d_w4, mt05d_w6= mt05d,  mtz05jz_w1, mtz05jz_w4, mtz05jz_w6 = mtz05jz)
```

```{r}
pls_w1 <- read_dta("../data/wave-1-(9-mo)/26_PLS_w1.dta") %>% 
  filter( pargen == 0)

pls_w4 <- read_excel("../data/wave-4-(18-mo)/PLS_W4_Final.xlsx") %>% 
  filter( pargen == 0)

pls_w6 <- read_excel("../data/wave-6-(24-mo)/PLS_W6.xlsx") %>%
  clean_names() %>% 
  filter( pargen_mom_0_dad_1 == 0) %>% 
  rename(pargen = pargen_mom_0_dad_1)

colSums(!is.na(pls_w6))
#57 of the plsacpr variable have actual data
sum(pls_w6$plsacpr >= 0)
```

```{r}
ignore_pls <- full_join(pls_w1, pls_w4, by = c("childid"), suffix = c("_w1", "_w4"))

pls_all <- full_join(ignore_pls, pls_w6, by = c("childid"))

```

```{r}
pls_all <- pls_all %>% 
  select(childid, plsecpr_w1, plsecpr_w4, plsecpr_w6 = plsecpr, plsacpr_w1, plsacpr_w4, plsacpr_w6 = plsacpr) 
```

```{r}
done <- full_join(pls_all, media_tech_all, by = c("childid")) 

done <- done %>% 
  mutate(ml_mean_w1 = (mt05c_w1 + mt05d_w1 + mtz05jz_w1)/3,
         ml_mean_w4 = (mt05c_w4 + mt05d_w4 + mtz05jz_w4)/3,
         ml_mean_w6 = (mt05c_w6 + mt05d_w6 + mtz05jz_w6)/3,
         plspr_mean_w1 = (plsecpr_w1 + plsacpr_w1)/2,
         plspr_mean_w4 = (plsecpr_w4 + plsacpr_w4)/2,
         plspr_mean_w6 = (plsecpr_w6 + plsacpr_w6)/2) %>% 
  glimpse()
```
Alrighty, so let's fix the datatypes, something that has helped me in the past is using the zap_labels(column_name) function to get rid of the double+label type, and then converting them with the as.factor() or as.numeric() functions. Then all NA's should just be NA, and for the missing data codes (-111, -222, etc) let's just turn them into NA.

```{r}
done <- done %>% 
  zap_labels(mt05c_w1, mt05c_w4, mt05c_w6, mt05d_w1, mt05d_w4, mt05d_w6, mtz05jz_w1, mtz05jz_w4, mtz05jz_w6)
#160 now 237
done <- done %>% 
  mutate(plsecpr_w1 = as.integer(plsecpr_w1),
         plsecpr_w4 = as.integer(plsecpr_w4),
         plsecpr_w6 = as.integer(plsecpr_w6),
         plsacpr_w1 = as.integer(plsacpr_w1),
         plsacpr_w4 = as.integer(plsacpr_w4),
         plsacpr_w6 = as.integer(plsacpr_w6),
         mt05c_w1 = as.integer(mt05c_w1),
         mt05c_w4 = as.integer(mt05c_w4),
         mt05c_w6 = as.integer(mt05c_w6),
         mt05d_w1 = as.integer(mt05d_w1),
         mt05d_w4 = as.integer(mt05d_w4),
         mt05d_w6 = as.integer(mt05d_w6),
         mtz05jz_w1 = as.integer(mtz05jz_w1),
         mtz05jz_w4 = as.integer(mtz05jz_w4),
         mtz05jz_w6 = as.integer(mtz05jz_w6))

done <- done %>% 
  replace_with_na(replace = list(plsecpr_w1 = c(-111, -222, -333, -444, -555, -666, -777, -888, -999)))
done <- done %>% 
  replace_with_na(replace = list(plsecpr_w4 = c(-111, -222, -333, -444, -555, -666, -777, -888, -999)))
done <- done %>% 
  replace_with_na(replace = list(plsecpr_w6 = c(-111, -222, -333, -444, -555, -666, -777, -888, -999)))
done <- done %>% 
  replace_with_na(replace = list(pleacpr_w1 = c(-111, -222, -333, -444, -555, -666, -777, -888, -999)))
done <- done %>% 
  replace_with_na(replace = list(plsacpr_w4 = c(-111, -222, -333, -444, -555, -666, -777, -888, -999)))
done <- done %>% 
  replace_with_na(replace = list(plsacpr_w6 = c(-111, -222, -333, -444, -555, -666, -777, -888, -999)))
done <- done %>% 
  replace_with_na(replace = list(plspr_mean_w1 = c(-111, -222, -333, -444, -555, -666, -777, -888, -999)))
done <- done %>% 
  replace_with_na(replace = list(plspr_mean_w4 = c(-111, -222, -333, -444, -555, -666, -777, -888, -999)))
done <- done %>% 
  replace_with_na(replace = list(plspr_mean_w6 = c(-111, -222, -333, -444, -555, -666, -777, -888, -999))) %>% 
  glimpse()
#done <- done %>% 
#  mutate(mtz05_mean_w1 = as.numeric(mtz05_mean_w1),
 #        mtz05_mean_w4 = as.numeric(mtz05_mean_w5),
  #       mtz05_mean_w6 = as.numeric(mtz05_mean_w6),
   #      plspr_mean_w1 = as.numeric(plspr_mean_w1),
    #     plspr_mean_w4 = as.numeric(plspr_mean_w4),
     #    plspr_mean_w6 = as.numeric(plspr_mean_w6))

```
Troubleshooting:

This counts the number of non-NA values in each column, once I know the number then I can check if it matches with the raw data(pls_w6).

```{r}
colSums(!is.na(done))
```
counts the number of NA values in each column of the dataframe
```{r}
colSums(is.na(done))
```

The codebook for wave 4 lists for the pls total
wave 4 mt05c n=302, I would expect then approx 151 observations for this variable in the done dataframe. In the done dataframe I have only 177 obs and 60 NA values = 237 obs so there are 65 observations that have just completely disappeared (according to wave 4 codebook)

Is it possoble another issue is that when calculating a mean if a value has NA the mean comes out as NA as well? We need to set the calculated means to ignore NA values.
  + no the number of non-na values match in the columns and the mean columns
  
  
  
  
```{r}
pls_long_mother <- read_dta("../data/PLS_long_father.dta")

```
  
  