

# Data

##libraries
```{r}
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)
library(magrittr)
library(ggcorrplot)
library(viridis)


library(tidyverse)
library(haven)
library(lme4)
library(lmerTest)
library(nlme)
```

## data loading
```{r}
pls <- readRDS("../data/pls_long_rank.dta")
bit_mother <- readRDS("../data/BIT_long_mother.dta")
bit_father <- readRDS("../data/BIT_long_father.dta")
bit <- readRDS("../data/BIT_long_par.dta")
demo <- readRDS("../data/demography.dta")
media <- readRDS("../data/media_long.dta")
grouping <- readRDS("../data/grouping_data.dta")
#hhincome, pargen, childid, parid
background <- read_dta("../data/wave-1-(9-mo)/2_BCK_w1.dta")
demographic_background <- read_dta("../data/wave-1-(9-mo)/1_DEM_w1.dta")
```

## data wrangling
```{r}

bg_income <- background %>% 
  zap_labels() %>% 
  transmute(par_id = as.character(parid),
            child_id = as.character(childid),
            hhincome = as.numeric(hhincome),
            household_income = hhincome/1000,
            father = as.logical(pargen))

bg_age <- demographic_background %>% 
  zap_labels() %>% 
  transmute(par_id = as.character(parid),
            child_id = as.character(childid),
            parent_age = as.numeric(parage),
            father = as.logical(pargen))


# if hhincome isn't a good predictor let's include bill_difficulty
demo <- demo %>% 
   transmute(par_id, 
             child_id, 
             bill_difficulty = as.factor(bill_difficulty),
             marital_status = as.factor(marital_status),
             assistance,
             father,
             par_us_born,
             highest_degree_completed,
             span_lang_form)

grouping <- grouping %>% 
  mutate(treatment = case_when(
    condition == "4" ~ " - control",
    condition == "1" ~ " - mom",
    condition == "2" ~ " - dad",
    condition == "3" ~ " - both"),
    treatment = fct_relevel(
      treatment,
      " - control",
      " - mom",
      " - dad",
      " - both"),
    control = ifelse(condition == "4", TRUE, FALSE))

pls <- pls %>%
  zap_labels() %>% 
  mutate(par_id = as.character(par_id),
         child_id = as.character(child_id))
 

media_pls <- media %>%
  full_join(bit, by = c("child_id", "wave")) %>% 
  full_join(pls, by = c("par_id", "child_id", "wave")) %>%
  inner_join(grouping, by = c("child_id")) %>%
  inner_join(demo, by = c("child_id", "par_id")) %>% 
  inner_join(bg_age, by = c("child_id", "par_id")) %>% 
  inner_join(bg_income, by = c("child_id", "par_id"))

media_pls_mother <- media %>%
  full_join(bit, by = c("child_id", "wave")) %>% 
  full_join(pls, by = c("par_id", "child_id", "wave")) %>%
  inner_join(grouping, by = c("child_id")) %>%
  inner_join(demo, by = c("child_id", "par_id")) %>%
  inner_join(bg_age, by = c("child_id", "par_id")) %>% 
  inner_join(bg_income, by = c("child_id", "par_id")) %>% 
  filter(par_id < 30000)

media_pls_father <- media %>%
  full_join(bit, by = c("child_id", "wave")) %>% 
  full_join(pls, by = c("par_id", "child_id", "wave")) %>%
  inner_join(grouping, by = c("child_id")) %>%
  inner_join(demo, by = c("child_id", "par_id")) %>%
  inner_join(bg_age, by = c("child_id", "par_id")) %>% 
  inner_join(bg_income, by = c("child_id", "par_id")) %>% 
  filter(par_id >= 30000)
```



# model

```{r}
model <- lmer(plspr ~ behavior_management:father:wave + condition + (1 | child_id), REML = FALSE, data = media_pls)

summary(model)
```

Main Effect Additions to Model:
Listed here are variables that need to be included in the model because they hold such important weight in the literature it’s non-negotiable
 * Parent_education
 * Parage
 * Nativity and/or lang_form (look out for collinearity, if it exists too just much select one)
 * Behavior_management


```{r}
#+ treatment + wave + par_us_born
model <- lmer(plspr ~ behavior_management  + parent_age + father  + span_lang_form + year_school_complete + behavior_management:treatment + (1 | child_id), REML = FALSE, data = media_pls)

summary(model)
```

```{r}
summary(media_pls$highest_degree_completed)
```
#HERE
```{r}
#hardly any difference b/w mothers and fathers (could test anova but the graph is pretty telling)
g <- media_pls %>%
  ggplot( aes(behavior_management, plspr)) +
  geom_point(aes(color = behavior_management)) +
  geom_smooth(method = "lm", color = "grey", size=0.7, se=FALSE) + 
  facet_grid(treatment~wave) +
  scale_color_viridis(option = "D") +
  xlab("Media as Behavior Management Frequency") +
  ylab("Infant Communication Skills") +
  theme_light() +
  ggtitle("Infant Communication Skills and Media as Behavior Management Across Waves")

g + theme(legend.position="none")
```
```{r}
ggplot(media_pls, aes(behavior_management, plspr))+
  geom_point(size = 1, aes(color = treatment)) +
  geom_smooth(aes(color = treatment, fill = treatment), method = "lm") + 
  scale_color_viridis(discrete = TRUE, option = "G")+
  scale_fill_viridis(discrete = TRUE) +
  facet_grid(treatment~wave)
```


```{r}
g<-media_pls %>%
  ggplot( aes(behavior_management, plspr, fill = treatment)) + 
  geom_boxplot() +
  geom_jitter() +
  xlab("Media Used as a Tool for Behavior Management") +
  ylab("Infant Communication Skills Percentile Rank") +
  labs(color = "BB Treatment") +
  facet_grid(~wave) +
  theme_bw() +
  ggtitle("Mean of PLS Percentile Rank across Waves Controlled by BB Treatment")

g + scale_fill_brewer(palette="RdBu") 
#later include year_school_complete and look at correlation
```

```{r}
#order the treatment 
 g <- media_pls %>%
  mutate(treatment = fct_reorder(treatment, plspr, .fun='median')) %>%
  ggplot( aes(x=reorder(treatment, plspr), y = plspr, fill = treatment)) + 
  geom_boxplot() +
  #geom_jitter() +
  xlab("Media Used as a Tool for Behavior Management") +
  ylab("Infant Communication Skills Percentile Rank") +
  labs(color = "BB Treatment") +
  facet_grid(~wave) +
  theme_minimal() +
  ggtitle("Mean of PLS Percentile Rank across Waves Controlled by BB Treatment")

g
#g + scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9")) 


#reorder(class, hwy),
#arrange(data, gclass)
```


```{r}
media_pls%>%
  ggplot() +
  aes(x = wave, y = plspr, group = child_id, color = treatment) +
  geom_point() +
  geom_line() +
  xlab("Waves (9mo and 24mo)") +
  ylab("PLS Scores") +
  ggtitle("Spaghetti Plot of PLS Scores") +
  labs(color = "total_s") +
  labs(color = "BB Treatment") +
  theme_bw() +
  facet_grid(father~treatment) +
  theme(
  #text = element_text(family = "Times"),
  plot.title = element_text(hjust = 0.5)
)
```
Is there a change in media management based of condition over time? 

Since behavior management is observed by both mothers and fathers should we seperate
```{r}
# is there a change in media management based of condition over time?
media_pls%>%
  ggplot() +
  aes(x = wave, y = behavior_management, group = child_id, color = treatment) +
  geom_point() +
  geom_line() +
  xlab("Waves (9mo and 24mo)") +
  ylab("Behavior Management") +
  ggtitle("Spaghetti Plot of Behavior Management Scores") +
  #labs(color = "total_s") +
  #labs(color = "BB Treatment") +
  theme_bw() +
  facet_grid(father~treatment) +
  theme(
  text = element_text(family = "Times"),
  plot.title = element_text(hjust = 0.5)
)
```
```{r}
interaction.plot(
x.factor = media_pls$wave,
trace.factor = media_pls$child_id,
response = media_pls$behavior_management,
type = "o",
xlab = "Waves",
ylab = "Behavior management",
lty = 1,
pch = 19,
legend = FALSE,
main = "Spaghetti Plot of Behavior Management"
)
```
### Hypothesis Testing
```{r}
g<-media_pls %>%
  filter(father == FALSE) %>% 
  ggplot( aes(x = treatment, y = behavior_management, color = treatment)) + 
  geom_boxplot() +
  geom_jitter() +
  xlab("BB Treatment") +
  ylab("Media as Behavior Management") +
  labs(color = "BB Treatment") +
  facet_grid(~wave) +
  theme_bw() +
  ggtitle("Media as Behavior Management across Waves Controlled by BB Treatment")

g + scale_fill_brewer(palette="RdBu") 
```

```{r}
bm_cond_w <- aov(behavior_management ~ treatment + wave, media_pls)

summary(bm_cond_w)
```
This anova table says there isn't enough evidence to conclude that mean behavior management within each treatment category are different from one another

Also, one mean of behavior_management across the different waves

##### Contingency Table of CHANGE in PLS and daily use Rec/Not Rec

```{r}
cont_table_bm_cond_w <- table(media_pls$treatment, media_pls$wave)
cont_table_bm_cond_w
```

##### Chi-Squared Test of Indepdendence

H0: pls_change and daily_use are independent (unrelated)
H1: PLs_change and daily_use are dependent (related)

```{r}
chisq.test(anova_table_no_double$pls_change_cat, anova_table_no_double$daily_use_cat)
```
