
```{r library}
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)
library(magrittr)
library(ggcorrplot)
```

# Data 
```{r}
media_data <- readRDS(file="../data/media_data.dta")
demography <- readRDS(file="../data/demography.dta")

bit_long_par <- readRDS(file="../data/BIT_long_par.dta")
bit_long_father <- readRDS(file="../data/BIT_long_father.dta")
bit_long_mother <- readRDS(file="../data/BIT_long_mother.dta")

bit_wide <- readRDS(file="../data/BIT_wide.dta")

media_long <- readRDS(file="../data/media_long.dta")
media_wide <- readRDS(file="../data/media_wide.dta")

pls_wide <- readRDS(file="../data/PLS_wide_mother.dta")
pls_wide_father <- readRDS(file="../data/PLS_wide_father.dta")
pls_long <- readRDS(file="../data/PLS_long_mother.dta")
pls_long_father <- readRDS(file="../data/PLS_long_father.dta")
```


```{r}
demo <- demo %>% 
  transmute(par_id, child_id, 
            bill_difficulty = as.factor(bill_difficulty),
            marital_status = as.factor(marital_status),
            assistance,
            father)

pls <- pls %>%
  mutate(par_id = as.character(par_id),
         child_id = as.character(child_id))

glimpse(media_pls)

media_pls <- media %>%
  full_join(bit, by = c("child_id", "wave")) %>% 
  full_join(pls, by = c("par_id", "child_id", "wave")) %>%
  inner_join(grouping, by = c("child_id")) %>%
  inner_join(demo, by = c("child_id", "par_id")) 

media_pls_mother <- media %>%
  full_join(bit, by = c("child_id", "wave")) %>% 
  full_join(pls, by = c("par_id", "child_id", "wave")) %>%
  inner_join(grouping, by = c("child_id")) %>%
  inner_join(demo, by = c("child_id", "par_id")) %>%
  filter(par_id < 30000)

media_pls_father <- media %>%
  full_join(bit, by = c("child_id", "wave")) %>% 
  full_join(pls, by = c("par_id", "child_id", "wave")) %>%
  inner_join(grouping, by = c("child_id")) %>%
  inner_join(demo, by = c("child_id", "par_id")) %>%
  filter(par_id >= 30000)
 

pls <- readRDS("../data/pls_long_rank.dta")
bit_mother <- readRDS("../data/BIT_long_mother.dta")
bit_father <- readRDS("../data/BIT_long_father.dta")
bit <- readRDS("../data/BIT_long_par.dta")
demo <- readRDS("../data/demography.dta")
media <- readRDS("../data/media_long.dta")
grouping <- readRDS("../data/grouping_data.dta")

glimpse(demo)
demo <- demo %>% 
  transmute(par_id, child_id, 
            bill_difficulty = as.factor(bill_difficulty),
            marital_status = as.factor(marital_status),
            assistance,
            father)

pls <- pls %>%
  mutate(par_id = as.character(par_id),
         child_id = as.character(child_id))

glimpse(media_pls)

media_pls <- media %>%
  full_join(bit, by = c("child_id", "wave")) %>% 
  full_join(pls, by = c("par_id", "child_id", "wave")) %>%
  inner_join(grouping, by = c("child_id")) %>%
  inner_join(demo, by = c("child_id", "par_id")) 

media_pls_mother <- media %>%
  full_join(bit, by = c("child_id", "wave")) %>% 
  full_join(pls, by = c("par_id", "child_id", "wave")) %>%
  inner_join(grouping, by = c("child_id")) %>%
  inner_join(demo, by = c("child_id", "par_id")) %>%
  filter(par_id < 30000)

media_pls_father <- media %>%
  full_join(bit, by = c("child_id", "wave")) %>% 
  full_join(pls, by = c("par_id", "child_id", "wave")) %>%
  inner_join(grouping, by = c("child_id")) %>%
  inner_join(demo, by = c("child_id", "par_id")) %>%
  filter(par_id >= 30000)
```

## Data for lmer assumption checking

```{r}
pls <- readRDS("../data/pls_long_rank.dta")
grouping <- readRDS("../data/grouping_data.dta")
media <- readRDS("../data/media_long.dta") %>% glimpse()

pls <- pls %>% 
  mutate(child_id = as.character(child_id))

pls_cond <- pls %>% 
  inner_join(grouping, by = c("child_id"))

bm <- media %>% 
  select(child_id, par_id, behavior_management, wave)

bm_cond <- media %>%
  inner_join(grouping, by = c("child_id")) %>%
  select(child_id, par_id, behavior_management, condition)

# pls by wave
pls_w1 <- pls %>% 
  filter(wave == 1) 
pls_w4 <- pls %>%
  filter(wave == 4)
pls_w6 <- pls %>% 
  filter(wave == 6)


# pls by condition
pls_cond_1 <- pls_cond %>%
  filter(condition == 1)
pls_cond_2 <- pls_cond %>%
  filter(condition == 2)
pls_cond_3 <- pls_cond %>%
  filter(condition == 3)
pls_cond_4 <- pls_cond %>%
  filter(condition == 4)


# behavior management by wave
bm_w1 <- bm %>%
  filter(wave == 1)
bm_w4 <- bm %>%
  filter(wave == 4)
bm_w6 <- bm %>%
  filter(wave == 6)

# behavior management by condition
bm_cond_1 <- bm_cond %>% 
  filter(condition == 1)
bm_cond_2 <- bm_cond %>% 
  filter(condition == 1)
bm_cond_3 <- bm_cond %>% 
  filter(condition == 1)
bm_cond_4 <- bm_cond %>% 
  filter(condition == 1)


```

# Assumptions for LMER
__We are currently dealing Linear-Mixed Effects Model with a Random Intercept (child_id) with a triple interaction term and a categorical fixed effect__

  1. Positively Correlated Clustered Measurements (Ex: mealtimes_w1 v mealtimes_w4) (a)
  2. Normality Distribution of Model Residuals/Error (c)
        + may apply a transform to achieve this
  3. Homoscedasiticity/Homogeneity of Residuals/Error Variance (b & c)
        + (same thing?) Constant Variance b/w Transformed Residuals & Transformed Predicted Value
  4. No autocorrelation (b)
  5. No Multicollinearity (b)
  
References:
  a. https://link.springer.com/article/10.1007/s41237-020-00130-8#:~:text=The%20LME%20incorrectly%20assumed%20a,estimated%20SEs%20under%20both%20models.
  b. https://bookdown.org/animestina/phd_july_19/testing-the-assumptions.html
  c. STATS 112 HW4

## Positively Correlated Clustered Measurements
Response: 
* plspr

Clustered by: 
* Wave (3 levels)
* Condition (4 levels)
* father

Data Variables Needed:

__Table 1:__
(Key) child_id
1. plspr_w1
2. plspr_w4
3. plspr_w6

```{r}


corr_pls_wave <-
```


__Table 2:__
(Key) child_id
4. plspr_cond1
5. plspr_cond2
6. plspr_cond3
7. plspr_cond4

__Table 3:__
(Key) child_id
8. behavior_management_w1
9. behavior_management_w4
10. behavior_management_w6

__Table 4:__
(Key) child_id
4. behavior_management_cond1
5. behavior_management_cond2
6. behavior_management_cond3
7. behavior_management_cond4

__Table 5:__
(Key) child_id
4. behavior_management_fatherTRUE
5. behavior_management_fatherFALSE

```{r}

```

Questions:
1. Do we need to include behavior-management in this analysis to see if it's positively correlated b/w clusters
  + "it assumes that observations within clusters are always positively correlated" (d)
  + based on that this statement we probably should check behavior management
  
References: 
 d. https://www.researchgate.net/publication/348750306_Small_and_negative_correlations_among_clustered_observations_limitations_of_the_linear_mixed_effects_model
## Normality Distribution of Model Residuals/Error (c)

## Homoscedasiticity/Homogeneity of Residuals/Error Variance (b & c)

## No autocorrelation (b)

## No Multicollinearity (b)


# Final Model
```{r}
# final significant found before we got tired
model <- lmer(plspr ~ behavior_management:father:wave + condition + (1 | child_id), REML = FALSE, data = media_pls)

summary(model)
```



# EDA
```{r}
ggplot(cplm_data,
       aes(x = ml_w1,
           y = ml_w4))  +
  geom_point() +
  geom_smooth(method = "lm")

  
ggplot(cplm_data,
       aes(x = acpr_w1,
           y = acpr_w4))  +
  geom_point() +
  geom_smooth(method = "lm")

```
```{r}
#correlation matrix of just mealtimes and auditory comprehension across all waves
corrplot(cor(cplm_data[,3:10]), order = "original", tl.col='black', tl.cex=.75) 
```
Need wide format data of all waves for (indented means variables have been included): 
 *    mealtimes 
 * behavior management
 * daily_use
 * total_score
 *    auditory_comprehension
 * expressive_communication
 * social-emotional_problem
 * social_emotional_competencies

Expressive Communication
```{r}

```

IDEA to consider if everything is bad:
Take average of each variable across all time points and assign clusters based off condition, see if correlations are positive then maybe we can build a model based off that instead of across waves.
