
The three variables in which we can hypothetically perform cross lagged analysis are mealtimes, discipline_behavior_management, and behavior_management.

```{r}
pls_wide_mother <- readRDS(file="../data/PLS_wide_mother.dta")
pls_wide_father <- readRDS(file="../data/PLS_wide_father.dta")
pls_long <- readRDS(file="../data/PLS_long_mother.dta")
pls_long_father <- readRDS(file="../data/PLS_long_father.dta")

pls_wide <- full_join(pls_wide_mother, pls_wide_father)
media_wide <- readRDS(file="../data/media_wide.dta")

```



First we need to look at the individual waves before we can move to cross lagged for mealtimes, discipline_behavior_management, and behavior_management.

```{r}
media_pls <- inner_join(media_wide, pls_wide, by = c("child_id", "par_id")) %>% filter(total_score.1 >0, total_score.4 > 0, total_score.6 >0)
```

mealtimes:
```{r}
mod1 <- lm(total_score.1 ~ mealtimes.1,  data = media_pls)
summary(mod1)

mod2 <- lm(total_score.4 ~ mealtimes.4,  data = media_pls)
summary(mod2)

mod3 <- lm(total_score.6 ~ mealtimes.6,  data = media_pls)
summary(mod3)
#Significant in wave 6

#reverse!

mod1 <- lm( mealtimes.1 ~total_score.1 ,  data = media_pls)
summary(mod1)

mod2 <- lm( mealtimes.4 ~total_score.4 ,  data = media_pls)
summary(mod2)

mod3 <- lm( mealtimes.6 ~total_score.6 ,  data = media_pls)
summary(mod3)
#Significant in wave 6 both ways

mod1 <- lm(mealtimes.4 ~ mealtimes.1,  data = media_pls)
summary(mod1)

mod2 <- lm(mealtimes.6 ~ mealtimes.4,  data = media_pls)
summary(mod2)

mod1 <- lm( total_score.4 ~total_score.1 ,  data = media_pls)
summary(mod1)

mod2 <- lm( total_score.6 ~total_score.4 ,  data = media_pls)
summary(mod2)


```

behavior_management:
```{r}
mod1 <- lm(total_score.1 ~ behavior_management.1,  data = media_pls)
summary(mod1)
mod2 <- lm(total_score.4 ~ behavior_management.4,  data = media_pls)
summary(mod2)
mod3 <- lm(total_score.6 ~ behavior_management.6,  data = media_pls)
summary(mod3)

#reverse!
mod1 <- lm( behavior_management.1~ total_score.1 ,  data = media_pls)
summary(mod1)
mod2 <- lm( behavior_management.4~total_score.4,  data = media_pls)
summary(mod2)
mod3 <- lm( behavior_management.6~total_score.6,  data = media_pls)
summary(mod3)
#Wave 4 and 6 is very significant both ways


mod1 <- lm(behavior_management.4 ~ behavior_management.1,  data = media_pls)
summary(mod1)
mod2 <- lm(behavior_management.6 ~ behavior_management.4,  data = media_pls)
summary(mod2)
mod3 <- lm(total_score.6 ~ behavior_management.6,  data = media_pls)
summary(mod3)
```


UHHHHHHHH Lines 70 - 200 are dealing with cross lagged between media and PLS


Lets start simple by looking across the waves with the variables we do have, 
mealtimes: going forward we will be looking at what we expect, wave 1 to 4 to 6 with mealtimes as a predictor of language scores

```{r}
#wave 1 to 4
mod1 <- lm(total_score.4 ~ mealtimes.1 + total_score.1,  data = media_pls)
summary(mod1)
#not significant
mod1 <- lm(mealtimes.4 ~ total_score.1 + mealtimes.1,  data = media_pls)
summary(mod1)

#wave 4 to 6
mod2 <- lm(total_score.6 ~ mealtimes.4 + total_score.4,  data = media_pls)
summary(mod2)
#p-value of 0.000418, very significant
mod1 <- lm(total_score.6 ~ mealtimes.4 + total_score.4,  data = media_pls)
summary(mod1)


#wave 1 to 6
mod3 <- lm(total_score.6 ~ mealtimes.1 + total_score.1,  data = media_pls)
summary(mod3)
#not significant... VERY INTERESTING

#reverse 
#wave 1 to 4
mod1 <- lm(mealtimes.1 ~ total_score.4 + mealtimes.4,  data = media_pls)
summary(mod1)

#wave 4 to 6
mod2 <- lm(mealtimes.4 ~ total_score.6 + mealtimes.6,  data = media_pls)
summary(mod2)

#wave 1 to 6
mod3 <- lm(mealtimes.1 ~ total_score.6 + mealtimes.6,  data = media_pls)
summary(mod3)
```

##BITprob
```{r}
bit_wide <- readRDS(file="../data/BIT_wide.dta")

media_bit <- inner_join(bit_wide, media_wide, by = c("child_id", "par_id"))
```


```{r}
mod1 <- lm(BITprobavg.2 ~ BITprobavg.5,  data = media_bit)
summary(mod1)
mod1 <- lm(BITprobavg.5 ~ BITprobavg.6,  data = media_bit)
summary(mod1)
#both significant

mod1 <- lm(BITprobavg.5 ~ mealtimes.1 + BITprobavg.2,  data = media_bit)
summary(mod1)
mod1 <- lm(BITprobavg.6 ~ mealtimes.4 + BITprobavg.5,  data = media_bit)
summary(mod1)

mod1 <- lm(mealtimes.4 ~ BITprobavg.2 + mealtimes.1,  data = media_bit)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ BITprobavg.5 + mealtimes.4,  data = media_bit)
summary(mod1)

```
##BITcompavg
```{r}
mod1 <- lm(BITcompavg.2 ~ BITcompavg.5,  data = media_bit)
summary(mod1)
mod1 <- lm(BITcompavg.5 ~ BITcompavg.6,  data = media_bit)
summary(mod1)

mod1 <- lm(BITcompavg.5 ~ mealtimes.1 + BITcompavg.2,  data = media_bit)
summary(mod1)
mod1 <- lm(BITcompavg.6 ~ mealtimes.4 + BITcompavg.5,  data = media_bit)
summary(mod1)

mod1 <- lm(mealtimes.4 ~ BITcompavg.2 + mealtimes.1,  data = media_bit)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ BITcompavg.5 + mealtimes.4,  data = media_bit)
summary(mod1)
```



Behavior management
```{r}
mod1 <- lm(behavior_management.4 ~ behavior_management.1, data = media_bit)
summary(mod1)
mod1 <- lm(behavior_management.6 ~ behavior_management.4, data = media_bit)
summary(mod1)
```

```{r}
#wave 1 to 4
mod1 <- lm(total_score.4 ~ behavior_management.1 + total_score.1,  data = media_pls)
summary(mod1)
#wave 1 is almost a good predictor, .059

#wave 4 to 6
mod2 <- lm(total_score.6 ~ behavior_management.4 + total_score.4,  data = media_pls)
summary(mod2)
#good model, p-value of 0.000923

#wave 1 to 6
mod3 <- lm(total_score.6 ~ behavior_management.1 + total_score.1,  data = media_pls)
summary(mod3)
#also good, p-value = 0.0314
```

Summary of mealtimes value: Within waves mealtimes only gives an association in wave 6. But when doing cross lagged association, only wave 4 mealtime was a significant predictor of wave 6 total score.x


##BITcompavg
```{r}
mod1 <- lm(BITcompavg.2 ~ BITcompavg.5,  data = media_bit)
summary(mod1)
mod1 <- lm(BITcompavg.5 ~ BITcompavg.6,  data = media_bit)
summary(mod1)

mod1 <- lm(BITcompavg.5 ~ behavior_management.1 + BITcompavg.2,  data = media_bit)
summary(mod1)
mod1 <- lm(BITcompavg.6 ~ behavior_management.4 + BITcompavg.5,  data = media_bit)
summary(mod1)

mod1 <- lm(behavior_management.4 ~ BITcompavg.2 + behavior_management.1,  data = media_bit)
summary(mod1)
mod1 <- lm(behavior_management.6 ~ BITcompavg.5 + behavior_management.4,  data = media_bit)
summary(mod1)
```


```{r}
mod1 <- lm(BITprobavg.5 ~ behavior_management.1 + BITprobavg.2,  data = media_bit)
summary(mod1)
mod1 <- lm(BITprobavg.6 ~ behavior_management.4 + BITprobavg.5,  data = media_bit)
summary(mod1)

mod1 <- lm(behavior_management.4 ~ BITprobavg.2 + behavior_management.1,  data = media_bit)
summary(mod1)
mod1 <- lm(behavior_management.6 ~ BITprobavg.5 + behavior_management.4,  data = media_bit)
summary(mod1)

mod1 <- lm(behavior_management.4 ~ BITprobavg.2 + behavior_management.1,  data = media_bit)
summary(mod1)
mod1 <- lm(behavior_management.6 ~ BITprobavg.5 + behavior_management.4,  data = media_bit)
summary(mod1)
```

```{r}
mod1 <- lm(total_score.4 ~ behavior_management.1 + total_score.1,  data = media_pls)
summary(mod1)
mod1 <- lm(total_score.6 ~ behavior_management.4 + total_score.4,  data = media_pls)
summary(mod1)

mod1 <- lm(behavior_management.4 ~ total_score.1 + behavior_management.1,  data = media_pls)
summary(mod1)
mod1 <- lm(behavior_management.6 ~ total_score.4 + behavior_management.4,  data = media_pls)
summary(mod1)

mod1 <- lm(behavior_management.4 ~ total_score.1 + behavior_management.1,  data = media_pls)
summary(mod1)
mod1 <- lm(behavior_management.6 ~ total_score.4 + behavior_management.4,  data = media_pls)
summary(mod1)
```



-----------------------------------------
gapminder, ggplot2, gganimate and gifski.
```{r}
#trash code :(
bleh <- bleh %>% 
  mutate(wave = as.integer(wave.x),
         daily_use = as.double(daily_use),
         total_score = as.double(total_score)) 

bleh %>% 
ggplot(gapminder, mapping = aes(x = daily_use, 
                      y= total_score, 
                      color = wave)) +
   geom_point(alpha = 0.7, show.legend = FALSE) +
   scale_size(range = c(2, 12)) +
   scale_x_log10() +
  facet_wrap(wave.x)

ggplot(data = demography, aes(x= household_income_numerical, 
                              y = years_school_complete)) +
  geom_point()
```

```{r}

```





#Okay im starting over>:(
father mealtime (if you want the moms just switch the > cause I'm not gonna do this agian lmao)
```{r}

media_bit_dad <- media_bit %>% 
  filter(par_id >25000)

mod1 <- lm(mealtimes.4 ~mealtimes.1, data = media_bit_dad)
summary(mod1)
mod1 <- lm(mealtimes.6 ~mealtimes.4, data = media_bit_dad)
summary(mod1)


mod1 <- lm(BITprobavg.5 ~BITprobavg.2, data = media_bit_dad)
summary(mod1)
mod1 <- lm(BITprobavg.6 ~BITprobavg.5, data = media_bit_dad)
summary(mod1)

mod1 <- lm(BITprobavg.5 ~ mealtimes.1 + BITprobavg.2, data = media_bit_dad)
summary(mod1)
mod1 <- lm(BITprobavg.6 ~ mealtimes.4 + BITprobavg.5, data = media_bit_dad)
summary(mod1)

mod1 <- lm(mealtimes.4 ~ BITprobavg.2 + mealtimes.1, data = media_bit_dad)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ BITprobavg.5 + mealtimes.4, data = media_bit_dad)
summary(mod1)

```

```{r}
media_bit_dad <- media_bit %>% 
  filter(par_id >25000)

mod1 <- lm(BITcompavg.5 ~BITcompavg.2, data = media_bit_dad)
summary(mod1)
mod1 <- lm(BITcompavg.6 ~BITcompavg.5, data = media_bit_dad)
summary(mod1)

mod1 <- lm(BITcompavg.5 ~ mealtimes.1 + BITcompavg.2, data = media_bit_dad)
summary(mod1)
mod1 <- lm(BITcompavg.6 ~ mealtimes.4 + BITcompavg.5, data = media_bit_dad)
summary(mod1)

mod1 <- lm(mealtimes.4 ~ BITcompavg.2 + mealtimes.1, data = media_bit_dad)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ BITcompavg.5 + mealtimes.4, data = media_bit_dad)
summary(mod1)

```

```{r}
media_pls_dad <- media_pls %>% 
  filter(par_id > 25000)

mod1 <- lm(mealtimes.4 ~ mealtimes.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ mealtimes.4, data = media_pls_dad)
summary(mod1)

mod1 <- lm(total_score.4 ~ total_score.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(total_score.6 ~ total_score.4, data = media_pls_dad)
summary(mod1)

mod1 <- lm(total_score.4 ~ mealtimes.1 + total_score.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(total_score.6 ~ mealtimes.4 + total_score.4, data = media_pls_dad)
summary(mod1)

mod1 <- lm(mealtimes.4 ~ total_score.1 + mealtimes.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ total_score.4 + mealtimes.4, data = media_pls_dad)
summary(mod1)
```

```{r}
media_pls_dad <- media_pls %>% 
  filter(par_id > 25000)

mod1 <- lm(mealtimes.4 ~ mealtimes.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ mealtimes.4, data = media_pls_dad)
summary(mod1)

mod1 <- lm(auditory_comprehension_score.4 ~ auditory_comprehension_score.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(auditory_comprehension_score.6 ~ auditory_comprehension_score.4, data = media_pls_dad)
summary(mod1)

mod1 <- lm(auditory_comprehension_score.4 ~ mealtimes.1 + auditory_comprehension_score.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(auditory_comprehension_score.6 ~ mealtimes.4 + auditory_comprehension_score.4, data = media_pls_dad)
summary(mod1)

mod1 <- lm(mealtimes.4 ~ auditory_comprehension_score.1 + mealtimes.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ auditory_comprehension_score.4 + mealtimes.4, data = media_pls_dad)
summary(mod1)

```

```{r}
media_pls_dad <- media_pls %>% 
  filter(par_id > 25000)

mod1 <- lm(mealtimes.4 ~ mealtimes.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ mealtimes.4, data = media_pls_dad)
summary(mod1)

mod1 <- lm(expressive_communication_score.4 ~ expressive_communication_score.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(expressive_communication_score.6 ~ expressive_communication_score.4, data = media_pls_dad)
summary(mod1)

mod1 <- lm(expressive_communication_score.4 ~ mealtimes.1 + expressive_communication_score.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(expressive_communication_score.6 ~ mealtimes.4 + expressive_communication_score.4, data = media_pls_dad)
summary(mod1)

mod1 <- lm(mealtimes.4 ~ expressive_communication_score.1 + mealtimes.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(mealtimes.6 ~ expressive_communication_score.4 + mealtimes.4, data = media_pls_dad)
summary(mod1)

```


--------------

#father behavior management

father mealtime
```{r}

media_bit_dad <- media_bit %>% 
  filter(par_id > 25000)

mod1 <- lm(behavior_management.4 ~behavior_management.1, data = media_bit_dad)
summary(mod1)
mod1 <- lm(behavior_management.6 ~behavior_management.4, data = media_bit_dad)
summary(mod1)


mod1 <- lm(BITprobavg.5 ~BITprobavg.2, data = media_bit_dad)
summary(mod1)
mod1 <- lm(BITprobavg.6 ~BITprobavg.5, data = media_bit_dad)
summary(mod1)

mod1 <- lm(BITprobavg.5 ~ behavior_management.1 + BITprobavg.2, data = media_bit_dad)
summary(mod1)
mod1 <- lm(BITprobavg.6 ~ behavior_management.4 + BITprobavg.5, data = media_bit_dad)
summary(mod1)

mod1 <- lm(behavior_management.4 ~ BITprobavg.2 + behavior_management.1, data = media_bit_dad)
summary(mod1)
mod1 <- lm(behavior_management.6 ~ BITprobavg.5 + behavior_management.4, data = media_bit_dad)
summary(mod1)

```

```{r}
media_bit_dad <- media_bit %>% 
  filter(par_id > 25000)

mod1 <- lm(BITcompavg.5 ~BITcompavg.2, data = media_bit_dad)
summary(mod1)
mod1 <- lm(BITcompavg.6 ~BITcompavg.5, data = media_bit_dad)
summary(mod1)

mod1 <- lm(BITcompavg.5 ~ behavior_management.1 + BITcompavg.2, data = media_bit_dad)
summary(mod1)
mod1 <- lm(BITcompavg.6 ~ behavior_management.4 + BITcompavg.5, data = media_bit_dad)
summary(mod1)

mod1 <- lm(behavior_management.4 ~ BITcompavg.2 + behavior_management.1, data = media_bit_dad)
summary(mod1)
mod1 <- lm(behavior_management.6 ~ BITcompavg.5 + behavior_management.4, data = media_bit_dad)
summary(mod1)

```

```{r}
media_pls_dad <- media_pls %>% 
  filter(par_id > 25000)

mod1 <- lm(behavior_management.4 ~ behavior_management.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(behavior_management.6 ~ behavior_management.4, data = media_pls_dad)
summary(mod1)

mod1 <- lm(total_score.4 ~ total_score.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(total_score.6 ~ total_score.4, data = media_pls_dad)
summary(mod1)

mod1 <- lm(total_score.4 ~ behavior_management.1 + total_score.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(total_score.6 ~ behavior_management.4 + total_score.4, data = media_pls_dad)
summary(mod1)

mod1 <- lm(behavior_management.4 ~ total_score.1 + behavior_management.1, data = media_pls_dad)
summary(mod1)
mod1 <- lm(behavior_management.6 ~ total_score.4 + behavior_management.4, data = media_pls_dad)
summary(mod1)
```


