---
title: "deborah-homoscedasticity"
author: "Deborah Franza"
date: "8/9/2022"
output: html_document
---
The motivation for using a robust estimation for a linear mixed-effects model is because of "contamination" that occurs in th model due to outliers.

The purpose of robust estimation is to provide estimates that are effected little by "contamination" and to detect and flag "contamination".

Key Points:
* no assumptions on grouping structure
      - is this a good thing? Determine what our grouping structure would be
*assumes correlated and uncorrelated random effects within levels
      - do we expect the child_id random intercept to have correlation?
      - or is it accounting for the correlations for each child_id's measurements

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Get libraries
```{r}
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)
library(magrittr)
library(ggcorrplot)
library(viridis)
library(haven)
library(lme4)
library(lmerTest)
library(nlme)
library(car) # for levene's test for Homo of Var
#install.packages("car")
require("lattice")
#install.packages("effects")
library(effects)
#install.packages("sjPlot")
library(sjPlot)
#install.packages("glmmTMB")
#install.packages("robustlmm")
#type in "no" when the question comes up. 


library(robustlmm)
```

#run this chunk for the data and model
```{r}
# copy from Chandra's 
pls <- readRDS("../data/pls_long_rank.dta")
bit_mother <- readRDS("../data/BIT_long_mother.dta")
bit_father <- readRDS("../data/BIT_long_father.dta")
bit <- readRDS("../data/BIT_long_par.dta")
demo <- readRDS("../data/demography.dta")
media <- readRDS("../data/media_long.dta")
grouping <- readRDS("../data/grouping_data.dta")



# demo <- demo %>% 
#   transmute(par_id, child_id, 
#             bill_difficulty = as.factor(bill_difficulty),
#             marital_status = as.factor(marital_status),
#             assistance,
#             father)

#library(naniar)
#vis_miss(demo)

grouping <- grouping %>% 
  mutate(treatment = case_when(
    condition == "4" ~ " - control",
    condition == "1" ~ " - mom",
    condition == "2" ~ " - dad",
    condition == "3" ~ " - both"),
    treatment = fct_relevel(
      treatment,
      " - control",
      " - mom",
      " - dad",
      " - both"),
    control = ifelse(condition == "4", TRUE, FALSE))

pls <- pls %>%
  mutate(par_id = as.character(par_id),
         child_id = as.character(child_id))
pls %>% 
  filter(wave == 6) %>% 
  nrow()

media_pls <- media %>%
  full_join(bit, by = c("child_id", "wave")) %>% 
  full_join(pls, by = c("par_id", "child_id", "wave")) %>%
  inner_join(grouping, by = c("child_id")) %>%
  inner_join(demo, by = c("child_id", "par_id"))

media_pls_mother <- media %>%
  full_join(bit, by = c("child_id", "wave")) %>% 
  full_join(pls, by = c("par_id", "child_id", "wave")) %>%
  inner_join(grouping, by = c("child_id")) %>%
  inner_join(demo, by = c("child_id", "par_id")) %>%
  filter(par_id < 30000)

media_pls_father <- media %>%
  full_join(bit, by = c("child_id", "wave")) %>% 
  full_join(pls, by = c("par_id", "child_id", "wave")) %>%
  inner_join(grouping, by = c("child_id")) %>%
  inner_join(demo, by = c("child_id", "par_id")) %>%
  filter(par_id >= 30000)
 
demographic_background <- read_dta("../data/wave-1-(9-mo)/1_DEM_w1.dta")
media_pls <- media_pls %>% 
  inner_join(transmute(demographic_background, par_age = parage,
    child_id = as.character(childid),
      par_id = as.character(parid)), by = c("child_id", "par_id"))

media_pls1 <- media_pls %>% 
  select(plspr, behavior_management, father,wave, treatment , par_age, years_school_complete, span_lang_form, child_id) %>% 
  na.omit()

model <- media_pls1 %>% 
  lmer(plspr ~ behavior_management+ father+wave+ treatment + par_age+ years_school_complete+ span_lang_form+ (1 | child_id), REML = FALSE, data = .)

summary(model)
```

#Reestimate the model with robust errors
```{r}
robustmodel <- media_pls1 %>% 
  rlmer(plspr ~ behavior_management+ father+wave+ treatment + par_age+ years_school_complete+ span_lang_form+ (1 | child_id), REML = FALSE, data = .)

summary(robustmodel)
```

Note there is a slight change in estimates and standard errors. 

```{r}
plot(robustmodel)

```
#What is robustness?
Robust statistics is statistics with good performance for data drawn from a wide range of probability distributions, especially for distributions that are not normal. 

#I Think
The closer to 1 the better, because higher robustness, the better the performance.

#All about the package I have been using 
https://cran.r-project.org/web/packages/robustlmm/vignettes/rlmer.pdf 
