__Conclusion is this assumption is violated.__
```{r}
#checking Linearity
model_linearity <- plot(resid(model),media_pls1$plspr)
```

### log transform on response still shows a pattern
```{r}
plot(resid(model),log(media_pls1$plspr))
```

### square transform on response still shows a pattern
```{r}
plot(resid(model),(media_pls1$plspr)^2)
```

```{r}
#checking Linearity
model_linearity <- plot(resid(model),(media_pls1$plspr)/2)
```


```{r}
plot(resid(model),1/(media_pls1$plspr))
#oof
```

```{r}
plot(resid(model),(media_pls1$plspr))
#oof
```

Now what if we say screw it and mess around with the inputs instead >:)

So in terms of doing a log transform the only predictors that we are allowed to 
do are behavior management, par_age, and years_school_complete
```{r}
#transform log behavior management
model_2.0 <- media_pls1 %>% 
  lmer(plspr ~ log(behavior_management)+ father+wave+ treatment + par_age+ years_school_complete+ span_lang_form+ (1 | child_id), REML = FALSE, data = .)
#plot 
plot(resid(model_2.0),(media_pls1$plspr))
```

```{r}
#transform log par_age
model_2.0 <- media_pls1 %>% 
  lmer(plspr ~ behavior_management+ father+wave+ treatment + log(par_age)+ years_school_complete+ span_lang_form+ (1 | child_id), REML = FALSE, data = .)
#plot 
plot(resid(model_2.0),(media_pls1$plspr))
```

```{r}
#transform log years_school_complete
model_2.0 <- media_pls1 %>% 
  lmer(plspr ~ behavior_management+ father+wave+ treatment + par_age+ log(years_school_complete)+ span_lang_form+ (1 | child_id), REML = FALSE, data = .)
#plot 
plot(resid(model_2.0),(media_pls1$plspr))
```

```{r}
#transform log all
model_2.0 <- media_pls1 %>% 
  lmer(plspr ~ log(behavior_management + par_age + years_school_complete)+ father+wave+ treatment + span_lang_form+ (1 | child_id), REML = FALSE, data = .)
#plot 
plot(resid(model_2.0),(media_pls1$plspr))
```


__Well what about square root transform__

```{r}
#transform log all
model_3.0 <- media_pls1 %>% 
  lmer(plspr ~ sqrt(behavior_management + par_age + years_school_complete)+ father+wave+ treatment + span_lang_form+ (1 | child_id), REML = FALSE, data = .)
#plot 
plot(resid(model_3.0),(media_pls1$plspr))
```

__Well what about 1/predictor__

```{r}
#transform log all
model_3.0 <- media_pls1 %>% 
  lmer(plspr ~ 1/(behavior_management + par_age + years_school_complete)+ father+wave+ treatment + span_lang_form+ (1 | child_id), REML = FALSE, data = .)
#plot 
plot(resid(model_3.0),(media_pls1$plspr))
```

__well what about predictor/2__
side note this code below does not work. sadge
```{r}
#transform 2/predict
model_3.0 <- media_pls1 %>% 
  lmer(plspr ~ behavior_management/2 + par_age/2 + years_school_complete/2+ father+wave+ treatment + span_lang_form+ (1 | child_id), REML = FALSE, data = .)
#plot 
plot(resid(model_3.0),(media_pls1$plspr))
```

```{r}
plot(resid(model),(media_pls1$plspr)) #original
plot(resid(model),(media_pls1$plspr)/2) #useless
plot(resid(model),log(media_pls1$plspr)) #change but bad
plot(resid(model),sqrt(media_pls1$plspr))# not too shabby?
plot(resid(model),1/(media_pls1$plspr)) #BAD

```



OKAY WAIT I HAVE AN IDEA, if we're changing the model output we can adjust the predictors by inverse!

```{r}
#sqrt:
#transform sqrt all
model_4.0 <- media_pls1 %>% 
  lmer(plspr ~ (behavior_management + par_age + years_school_complete)^2+ father+wave+ treatment + span_lang_form+ (1 | child_id), REML = FALSE, data = .)
#plot 
plot(resid(model_4.0),sqrt(media_pls1$plspr))
#HEyyyy, not too bad i think
plot(resid(model),media_pls1$plspr)
cor(resid(model),media_pls1$plspr)
cor(resid(model_2.0),(media_pls1$plspr))

```

```{r}
#log:
#transform 10^ for all
model_4.0 <- media_pls1 %>% 
  lmer(plspr ~ 10^(behavior_management) + par_age + years_school_complete+ father+wave+ treatment + span_lang_form+ (1 | child_id), REML = FALSE, data = .)
#note, this did not work
#plot 
plot(resid(model_4.0),log(media_pls1$plspr))
#HEyyyy, not too bad i think
```

im losing hope so i guess we can try changing the predictor
```{r}
#log:
model_5.0 <- media_pls1 %>% 
  lmer(log(plspr) ~ behavior_management + par_age + years_school_complete+ father+wave+ treatment + span_lang_form+ (1 | child_id), REML = FALSE, data = .)
#note, this did not work
#plot 
plot(resid(model_5.0),(media_pls1$plspr))
#HEyyyy, not too bad i think
cor(resid(model_5.0),(media_pls1$plspr))
model_5.0
```

```{r}
#sqrt:
model_5.0 <- media_pls1 %>% 
  lmer(sqrt(plspr) ~ (behavior_management + par_age + years_school_complete)^2+ father+wave+ treatment + span_lang_form+ (1 | child_id), REML = FALSE, data = .)
#note, this did not work
#plot 
plot(resid(model_5.0),(media_pls1$plspr))
#HEyyyy, not too bad i think
cor(resid(model_5.0),(media_pls1$plspr))
```

```{r}
#sqrt:
model_5.0 <- media_pls1 %>% 
  lmer(1/(plspr) ~ behavior_management + par_age + years_school_complete+ father+wave+ treatment + span_lang_form+ (1 | child_id), REML = FALSE, data = .)
#note, this did not work
#plot 
plot(resid(model_5.0),(media_pls1$plspr))
#HEyyyy, not too bad i think
cor(resid(model_5.0),(media_pls1$plspr))
```

