---
title: "models-aubree"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)
library(ggcorrplot)
```



```{r}
## Run to get all data

bitsea_w2 <- readRDS(file="../data/model_w2.dta")
bitsea_w6 <- readRDS(file="../data/model_w6.dta")
valuable_dataset <- readRDS(file="../data/valuable_dataset.dta")


pls_w1 <- readRDS(file="../data/PLS_wave_1.dta")
pls_w4 <- readRDS(file="../data/PLS_w4.dta")
pls_w6 <- readRDS(file="../data/PLS_w6.dta")

bitsea_w2 <- readRDS(file="../data/BITSEA_wave_2.dta")
bitsea_w5 <- readRDS(file="../data/bitsea_w5.dta")
bitsea_w6 <- readRDS(file="../data/BITSEA_wave_6.dta")

valuable_dataset <- readRDS(file="../data/valuable_dataset.dta")


demography <- readRDS(file="../data/demography.dta")
bitsea_data <- readRDS(file="../data/BIT_data.dta")
media_data <- readRDS(file="../data/media_data.dta")


media_data <- readRDS(file="../data/media_data.dta")
demography <- readRDS(file="../data/demography.dta")

pls_long <- readRDS(file="../data/PLS_long.dta")
bit_long_par <- readRDS(file="../data/BIT_long_par.dta")
bit_long_father <- readRDS(file="../data/BIT_long_father.dta")
bit_long_mother <- readRDS(file="../data/BIT_long_mother.dta")

pls_wide <- readRDS(file="../data/PLS_wide.dta")
bit_wide <- readRDS(file="../data/BIT_wide.dta")

media_long <- readRDS(file="../data/media_long.dta")
media_wide <- readRDS(file="../data/media_wide.dta")

```


```{r}
## Predicting Model (PLS score)
library(leaps)

pls_and_media <- full_join(media_data, pls_long, by = c("par_id", "child_id"))
head(pls_and_media)

pls_and_media <- 
  pls_and_media %>% 
  mutate(total_score = as.integer(total_score),
         id = as.character(id),
         auditory_comprehension_score = as.integer(auditory_comprehension_score),
         daily_use = as.integer(daily_use),
         educational_benefits = as.integer(educational_benefits),
         positive_beliefs_media = as.integer(positive_beliefs_media),
         ) %>% 
  filter(total_score != -666,
         total_score != -777,
         total_score != -888,
         total_score != -999)

#income_variable <- select(valuable_dataset, c("household_income_numerical", "par_id", "child_id"))
#pls_and_media <- full_join(pls_and_media, income_variable, by = c("child_id", "par_id"))

pls_and_media <- select(pls_and_media, -c("expressive_communication_score", "child_id", "par_id","id"))

#pls_and_media <- 
#na.omit(pls_and_media$household_income_numerical)

glimpse(pls_and_media)




sapply(lapply(pls_and_media, unique), length)

regfit.full = regsubsets(total_score ~., pls_and_media, method = "forward") 
reg.summary = summary(regfit.full)
names(reg.summary)


par(mfrow = c(2,2))
plot(reg.summary$rss, xlab = "Models", 
     ylab = "RSS", type= "l")
which.min(reg.summary$rss)
points(9, reg.summary$rss[9], col="red",cex=2 ,pch =20)


plot( reg.summary$adjr2, xlab = "Models", 
      ylab = "Adjusted RSQ", type= "l")

which.max(reg.summary$adjr2)
points(8, reg.summary$adjr2[8], col="red",cex=2 ,pch =20)

plot(reg.summary$cp, xlab= "Models", ylab= "CP"
     , type = 'l')
which.min(reg.summary$cp)
points(8, reg.summary$cp[8], col="red", cex=2, pch =20)



plot(reg.summary$bic, xlab= "Models", ylab= "BIC"
     , type = 'l')
which.min(reg.summary$bic)
points(8, reg.summary$bic[8], col="red", cex=2, pch =20)

coef(regfit.full, 8)


train = sample(c(TRUE,FALSE), nrow(pls_and_media), rep =TRUE)
test= (!train)
regfit.best=regsubsets(total_score~., data = pls_and_media[train,])
test.mat=model.matrix(total_score~ ., data = pls_and_media[test,])
val.errors= rep(NA, 9)
for(i in 1:9){
  coefi=coef(regfit.best, id=i)
  pred =test.mat[, names(coefi)]%*%coefi
  val.errors[i]= mean((pls_and_media$total_score[test]-pred)^2)
}

## dimensions are not the same... cant figure out how to fix. 


head(pls_and_media$total_score[test])
coefi=coef(regfit.best, id=i)
  pred =test.mat[, names(coefi)]%*%coefi
dim(pred)

log(val.errors)
which.min(val.errors)
```

cross lag models 
```{r}
## compared daily use from wave 1 to PLS score from wave 4. Note that we cannot
## account for media wave 4. This model will have to be updated. We seperated
## between mom and dad.
model1_data <- inner_join(pls_w4, pls_w1, by = c("child_id"), suffix = c("_w4", "_w1"))

model1_data <- inner_join(model1_data, media_data, by = c("child_id"))

model1_data <- filter(model1_data, 
                      total_score_w4 > 0)

model1_data_mom <- filter(model1_data, 
                          father == "FALSE")

model1_data_dad <- filter(model1_data, 
                          father == "TRUE")

model1_mom <- lm(total_score_w4 ~ daily_use + total_score_w1, data = model1_data_mom)
summary(model1_mom)

model1_dad <- lm(total_score_w4 ~ daily_use + total_score_w1, data = model1_data_dad)
summary(model1_dad)
```
From this model we see that media use from wave 1 (media_use) is a viable 
predictor when we are predicting PLS scores from wave 4 (total_score_w4), 
for both moms and dads. 
We know this because the p-value is less than .05. We accounted for the 
individual themselves by adding on the PLS score from wave 1(total_score_w1), 
even though we see it is not significant since the p-value is grater than .05. 


```{r}
##compared daily use from wave 1 to PLS score from wave 6. We seperated
## between mom and dad.
media_pls_w1_w6_mom <- inner_join(media_w1_w6, pls_w1_w6, 
                              by = c("par_id", "child_id")) %>% 
  filter(total_score_w6 > 0,
         father =="FALSE")

media_pls_w1_w6_dad <- inner_join(media_w1_w6, pls_w1_w6, 
                              by = c("par_id", "child_id")) %>% 
  filter(total_score_w6 > 0,
         father =="TRUE")

mod2_mom <- lm(total_score_w6 ~ daily_use_w1 + total_score_w1, data = media_pls_w1_w6_mom)
summary(mod2_mom)

mod2_dad <- lm(total_score_w6 ~ daily_use_w1 + total_score_w1, data = media_pls_w1_w6_dad)
summary(mod2_dad)
```
From this model we see that media use from wave 1 (media_use) is a viable 
predictor when we are predicting PLS scores from wave 6 (total_score_w6), 
only for moms!  
We know this because the p-value is less than .05. We accounted for the 
individual themselves by adding on the PLS score from wave 1(total_score_w1), 
even though we see it is not significant since the p-value is grater than .05. 
This implies that dad's assessment of media use is NOT a viable predictor for 
PLS scores from wave 6. 



Linear Mixed Effects model 
```{r}
media_long <- media_long %>% 
  mutate(wave = as.factor(wave)) %>% 
  filter(par_id < 25000)
pls_long
long_boi <- full_join(media_long, pls_long, by = c("child_id", "par_id", "wave")) %>% 
  filter(wave != 4,
         total_score > 0)



  #aubrees idea
library(lme4)
library(lmerTest)
model <- lmer(total_score ~ daily_use * wave + (1|child_id), data = long_boi)
summary(model)

```
## finding residual for model
```{r}
residual_model = predict(model) - long_boi$total_score
plot(residual_model, xlab = "child_id")


```


Nick's Models I copies over 
```{r}
media_w1_w6 <- inner_join(media_w1, media_w6, by = c("par_id", "child_id"), 
                          suffix = c("_w1", "_w6"))

pls_w1_w6 <- inner_join(PLS_w1, PLS_w6, by = c("par_id", "child_id"), 
                        suffix = c("_w1", "_w6"))

media_pls_w1_w6_mom <- inner_join(media_w1_w6, pls_w1_w6, 
                              by = c("par_id", "child_id")) %>% 
  filter(total_score_w6 > 0,
         father =="FALSE")

media_pls_w1_w6_dad <- inner_join(media_w1_w6, pls_w1_w6, 
                              by = c("par_id", "child_id")) %>% 
  filter(total_score_w6 > 0,
         father =="TRUE")

mod1 <- lm(daily_use_w6 ~ total_score_w1 + daily_use_w1,  data = media_pls_w1_w6)
summary(mod1)

```

