```{r}
library(tidyverse)
library(haven)

PLS_data <- readRDS(file="../data/PLS_data.dta")
BIT_data <- readRDS(file="../data/BIT_data.dta")
media_wave_1 <- readRDS(file="../data/media_wave_1.dta")
media_wave_6 <- readRDS(file="../data/media_wave_6.dta")
demography <- readRDS(file="../data/demography.dta")
media_long <- readRDS(file="../data/media_long.dta")
pls_long <- readRDS(file="../data/PLS_long.dta")
```

## wave 1 to wave 6 media to pls - for mom and dad

### subsetting data
```{r}
pls_mom_1 <- pls_long %>% 
  filter(par_id < 30000, wave == 1) %>%
  select(par_id, total_score)

pls_mom_6 <- pls_long %>% 
  filter(par_id < 30000, wave == 6) %>%
  select(par_id, total_score)

pls_mom <- pls_mom_1 %>% 
  inner_join(pls_mom_6, by = c("par_id"), suffix = c("_w1", "_w6"))


  
pls_dad_1 <- pls_long %>%
  filter(par_id > 30000, wave == 1) %>%
  select(par_id, total_score)
  
pls_dad_6 <- pls_long %>%
  filter(par_id > 30000, wave == 6) %>%
  select(par_id, total_score)

pls_dad <- pls_dad_1 %>% 
  inner_join(pls_dad_6, by = c("par_id"), suffix = c("_w1", "_w6"))



media_mom_1 <- media_long %>%
  filter(par_id < 30000, wave == 1) %>% 
  select(par_id, daily_use)

media_mom_6 <- media_long %>%
  filter(par_id < 30000, wave == 6) %>% 
  select(par_id, daily_use)

media_mom <- media_mom_1 %>% 
  inner_join(media_mom_6, by = c("par_id"), suffix = c("_w1", "_w6"))



media_dad_1 <- media_long %>% 
  filter(par_id > 30000, wave == 1) %>% 
  select(par_id, daily_use)

media_dad_6 <- media_long %>% 
  filter(par_id > 30000, wave == 6) %>% 
  select(par_id, daily_use)

media_dad <- media_dad_1 %>% 
  inner_join(media_dad_6, by = c("par_id"), suffix = c("_w1", "_w6"))


mom_data <- pls_mom %>%
  inner_join(media_mom, by = c("par_id")) %>% 
  na.omit()

dad_data <- pls_dad %>%
  inner_join(media_dad, by = c("par_id")) %>% 
  na.omit()

mom_data

dad_data
```

## mom - media vs pls - wave 1 to wave 6 - cross lag linear regression model

```{r}
# linear relationship between wave 1 media involvement vs wave 6 total score
# controlling for total score
summary(lm(total_score_w6 ~ daily_use_w1 + total_score_w1, data = mom_data))
```

```{r}
# linear relationship between wave 1 total score vs wave 6 media involvement
# controlling for media involvement
summary(lm(daily_use_w6 ~ total_score_w1 + daily_use_w1, data = mom_data))
```


## dad - media vs pls - wave 1 to wave 6 - cross lag linear regression model

```{r}
# linear relationship between wave 1 media involvement vs wave 6 total score
# controlling for total score
summary(lm(total_score_w6 ~ daily_use_w1 + total_score_w1, data = dad_data))
```

```{r}
# linear relationship between wave 1 total score vs wave 6 media involvement
# controlling for media involvement
summary(lm(daily_use_w6 ~ total_score_w1 + daily_use_w1, data = dad_data))
```

## multi unconditional means model

### grand means (null) model (step 1): checking response without any predictors

model:

logLik: model fit - lower the better
Random effects: 
  StdDev Intercept and residual 
  - helps calculates intra-class correlation coefficient??
    - intercept^2 / (intercept^2 + residual^2)
    - percentage of variability
      - flush it out by selecting a proper slope
      - add predictors to see if we can account for the variability
    - larger values means more clustering
    - more clustering is a sign to use multilevel modeling
  - shows how much clustering exists within our data
  - multilevel analysis
Fixed effects:
  - check difference between intercept vs p-value which is (0)


intervals(model)

fixed effects:
- shows estimate + lower and upper bound of 95% CI
- estimate of intercept along with it's CI

random effects:
- shows how individuals vary
- ensure lower bound is not the only negative value


```{r}
library(nlme)
pls_long <- readRDS(file="../data/PLS_long.dta")

pls_long <- pls_long %>%
  mutate(wave = case_when(
    wave == "1" ~ 0,
    wave == "4" ~ 1,
    wave == "6" ~ 2
  )) %>%
  filter(if_all(where(is.numeric), ~ .x > 0))

mod0 <- lme(total_score ~ 1, random = ~ 1 | child_id, data = pls_combined, method = "ML")

# Log-like: -3576.387
# estimated intercept 94.31003
mod0

# intercept 94.3 compared to 0
summary(mod0)

intervals(mod0)

# ICC (intraclass correlation coefficient) = 63%
(12.17565^2) / (12.17565^2 + 9.13523^2)
```

## Unconditional growth model (setting up slope)

### checking xyplot for variability in slope accross individuals

```{r}
library(lattice)

xyplot(total_score ~ wave | child_id, data = pls_long, type = c("p", "r"))

```

```{r}
# unconditional growth with time as a fixed slope

mod_fs <- lme(total_score ~ wave, random = ~ 1 | child_id, data = pls_combined, method = "ML")

# log-like: -469.2703
mod_fs

# intercept 95 vs 0
summary(mod_fs)

# wave is significant as a fixed effect
intervals(mod_fs)

# ICC (intraclass correlation coefficient) = 100% ????????????
(12.44946^2) / (12.44946^2 + 4.880886e-15^2)
```

```{r}
# unconditional growth with time as a random slope

media_long <- readRDS(file="../data/media_long.dta")

combined_data <- media_long %>%
  filter(par_id < 30000) %>%
  select(par_id, daily_use) %>%
  inner_join(pls_long, by = c("par_id")) %>%
  na.omit()

mod_fs <- lme(total_score ~ wave, random = ~ wave | child_id, data = pls_combined, method = "ML")

# log-like: -3536.516
mod_fs

# intercept 96.62
summary(mod_fs)


intervals(mod_fs)

# ICC - 65%
(11.95052^2) / (11.95052^2 + 8.696666^2)
```


## lme4 - unconditional mean

```{r}
library(lme4)
library(lmerTest)

# null model
mod_null <- lmer(total_score + 1 ~ (1 | child_id), data = data_combined)

summary(mod_null)
  
```



```{r}
mod_1 <- lmer(total_score ~ wave * daily_use + (1 | child_id), data = data_combined)

summary(mod_1)
```


```{r}
# distribution of total score

pls_long %>%
  ggplot(aes(total_score)) +
  geom_histogram(binwidth = 1)

```

```{r}
# negative values
pls_long %>%
  filter(if_any(where(is.numeric), ~ .x < 0))
```

```{r}
# distribution of total score without negative values
pls_long %>%
  filter(if_all(where(is.numeric), ~ .x > 0)) %>%
  ggplot(aes(total_score)) +
  geom_histogram(binwidth = 1)

```

```{r}
# why don't we have data from wave 1?
pls_long %>%
  filter(if_all(where(is.numeric), ~ .x > 0))
```

```{r}
# show na values
pls_long %>%
  filter_all(any_vars(is.na(.)))
```

```{r}
pls1 <- read_dta("../data/wave-1-(9-mo)/26_PLS_w1.dta")
pls4 <- read_excel("../data/wave-4-(18-mo)/PLS_W4_Final.xlsx", sheet = 4)
pls6 <- read_excel("../data/wave-6-(24-mo)/PLS_W6.xlsx", sheet = 3)
media1 <- read_dta("../data/wave-1-(9-mo)/10_MT_w1.dta")
media6 <- read_dta("../data/wave-6-(24-mo)/BB2_W6-MT.dta")

pls1 <- pls1 %>% 
  transmute(child_id = as.character(childid),
            par_id = as.character(parid),
            wave = as.character(wave),
            auditory_score = plsacss,
            expressive_score = plsecss,
            total_score = plsss)

pls4 <- pls4 %>%
  transmute(child_id = as.character(childid),
            par_id = as.character(parid),
            wave = as.character(wave),
            auditory_score = plsacss,
            expressive_score = plsecss,
            total_score = plsss) %>%
  filter(if_all(where(is.numeric), ~ .x > 0))

pls6 <- pls6 %>%
  transmute(child_id = as.character(childid),
            par_id = as.character(parid),
            wave = as.character(wave),
            auditory_score = plsacss,
            expressive_score = plsecss,
            total_score = plsss) %>%
  filter(if_all(where(is.numeric), ~ .x > 0))

pls_combined <- rbind(pls1, pls4, pls6) %>%
  mutate(wave = case_when(
    wave == "1" ~ 0,
    wave == "6" ~ 1
  ))

media1 <- media1 %>%
  transmute(child_id = as.character(childid),
            par_id = as.character(parid),
            wave = as.character(wave),
            daily_use = MTdailyuse)

media6 <- media6 %>%
  transmute(child_id = as.character(childid),
            par_id = as.character(parid),
            wave = as.character(wave),
            daily_use = MTdailyuse)

media_combined <- rbind(media1, media6) %>%
  filter(par_id >= 30000) %>%
  mutate(wave = case_when(
    wave == "1" ~ 0,
    wave == "62" ~ 1,
  ))

data_combined <- pls_combined %>%
  inner_join(media_combined, by = c("par_id", "child_id", "wave")) %>%
  na.omit()

nrow(pls_combined)

# no na values
sum(is.na(pls_combined))

# no negative values
pls_combined %>%
  filter(if_any(where(is.numeric), ~ .x < 0))
```

