
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Loading code
```{r include=FALSE}
library(forcats)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(janitor)
```

```{r}
media_data <- readRDS(file="../data/media_data.dta")
demography <- readRDS(file="../data/demography.dta")

pls_long <- readRDS(file="../data/PLS_long.dta")
bit_long_par <- readRDS(file="../data/BIT_long_par.dta")
bit_long_father <- readRDS(file="../data/BIT_long_father.dta")
bit_long_mother <- readRDS(file="../data/BIT_long_mother.dta")

pls_wide <- readRDS(file="../data/PLS_wide.dta")
bit_wide <- readRDS(file="../data/BIT_wide.dta")

media_long <- readRDS(file="../data/media_long.dta")
media_wide <- readRDS(file="../data/media_wide.dta")
```

```{r include=FALSE}
bitsea_w2 <- readRDS(file="../data/model_w2.dta")
bitsea_w5 <- readRDS(file="../data/wave_5.dta")
bitsea_w6 <- readRDS(file="../data/model_w6.dta")

PLS_w1 <- readRDS(file = "../data/scores_w1.dta")
PLS_w4 <- readRDS(file="../data/PLS_w4.dta")
PLS_w6 <- readRDS(file="../data/PLS_w6.dta")

media_w1 <- readRDS(file="../data/media_data.dta")
#media_w4 <- readRDS(file= "../data/")
media_w6 <- readRDS(file="../data/media_wave_6.dta")

valuable_dataset <- readRDS(file="../data/valuable_dataset.dta")


```

#preliminary EDA

the relationship between media involvment and daily use for the wave itself is not significant as seen below
```{r}
#dad
media_pls_w1 <- inner_join(PLS_w1, media_w1, by = c("par_id", "child_id")) %>% 
  filter(par_id > 25000)

mod3d <- lm(total_score ~ daily_use, data = media_pls_w1)
summary(mod3d)
#mom
media_pls_w1 <- inner_join(PLS_w1, media_w1, by = c("par_id", "child_id")) %>% 
  filter(par_id < 25000)

mod3m <- lm(total_score ~ daily_use, data = media_pls_w1)
summary(mod3m)

#dad
media_pls_w6 <- inner_join(PLS_w6, media_w6, by = c("par_id", "child_id"))%>% 
  filter(par_id > 25000)

mod4d <- lm(total_score ~ daily_use, data = media_pls_w6)
summary(mod4d)

#mom
media_pls_w6 <- inner_join(PLS_w6, media_w6, by = c("par_id", "child_id"))%>% 
  filter(par_id < 25000)

mod4m <- lm(total_score ~ daily_use, data = media_pls_w6)
summary(mod4m)
```

#wave 1 and 4 media/pls
```{r}
media_w1_w4 <- inner_join(media_w1, media_w4, by = c("par_id", "child_id"), 
                          suffix = c("_w1", "_w4"))

pls_w1_w4 <- inner_join(PLS_w1, PLS_w4, by = c("par_id", "child_id"), 
                        suffix = c("_w1", "_w4"))

media_pls_w1_w4 <- inner_join(media_w1_w4, pls_w1_w4, 
                              by = c("par_id", "child_id")) %>% 
  filter(total_score_w4 > 0 )

mod1 <- lm(daily_use_w4 ~ total_score_w1 + daily_use_w1,  data = media_pls_w1_w4)
summary(mod1)

mod2 <- lm(total_score_w4 ~ daily_use_w1 + total_score_w1, data = media_pls_w1_w4)
summary(mod2)

```

#wave 4 and 6 media/pls
```{r}
media_w4_w6 <- inner_join(media_w4, media_w6, by = c("par_id", "child_id"), 
                          suffix = c("_w4", "_w6"))

pls_w4_w6 <- inner_join(PLS_w4, PLS_w6, by = c("par_id", "child_id"), 
                        suffix = c("_w4", "_w6"))

media_pls_w4_w6 <- inner_join(media_w4_w6, pls_w4_w6, 
                              by = c("par_id", "child_id")) %>% 
  filter(total_score_w6 > 0 )

mod1 <- lm(daily_use_w6 ~ total_score_w4 + daily_use_w4,  data = media_pls_w4_w6)
summary(mod1)

mod2 <- lm(total_score_w6 ~ daily_use_w4 + total_score_w4, data = media_pls_w4_w6)
summary(mod2)
```

#wave 1 and 6 media/pls
```{r}
media_w1_w6 <- inner_join(media_w1, media_w6, by = c("par_id", "child_id"), 
                          suffix = c("_w1", "_w6"))

pls_w1_w6 <- inner_join(PLS_w1, PLS_w6, by = c("par_id", "child_id"), 
                        suffix = c("_w1", "_w6"))

media_pls_w1_w6 <- inner_join(media_w1_w6, pls_w1_w6, 
                              by = c("par_id", "child_id")) %>% 
  filter(total_score_w6 > 0 )

```

```{r}
#dad wave 1 and 6 model
dad_media_pls_w1_w6 <- inner_join(media_w1_w6, pls_w1_w6, 
                              by = c("par_id", "child_id")) %>% 
  filter(total_score_w6 > 0, par_id > 25000)
dmod1 <- lm(daily_use_w6 ~ total_score_w1 + daily_use_w1,  data = dad_media_pls_w1_w6)
summary(dmod1)

#mom wave 1 and 6 model
mom_media_pls_w1_w6 <- inner_join(media_w1_w6, pls_w1_w6, 
                              by = c("par_id", "child_id")) %>% 
  filter(total_score_w6 > 0, par_id < 25000)
mmod1 <- lm(daily_use_w6 ~ total_score_w1 + daily_use_w1,  data = mom_media_pls_w1_w6)
summary(mmod1)

#BOTH
mod1 <- lm(daily_use_w6 ~ total_score_w1 + daily_use_w1,  data = media_pls_w1_w6)
summary(mod1)
```
Total score from wave 1 is not a good predictor for daily use in wave 6

```{r}
#dad
dmod2 <- lm(total_score_w6 ~ daily_use_w1 + total_score_w1 , data = dad_media_pls_w1_w6)
summary(dmod2)

#mom
mmod2 <- lm(total_score_w6 ~ daily_use_w1 + total_score_w1 , data = mom_media_pls_w1_w6)
summary(mmod2)

#BOTH 
mod2 <- lm(total_score_w6 ~ daily_use_w1 + total_score_w1 , data = media_pls_w1_w6)
summary(mod2)
```
daily use from wave 1 IS a good predictor of total score in wave 6 but only for mothers 


#Linear Mixed Effects Model

Now we need long format
```{r}
media_long <- media_long %>% 
  filter(par_id < 25000)
pls_long
long_boi <- full_join(media_long, pls_long, by = c("child_id", "par_id", "wave")) %>% 
  filter(wave != 4,
         total_score > 0)



  #aubrees idea
install.packages("lme4")
install.packages("lmerTest")
library(lme4)
library(lmerTest)
model <- lmer(total_score ~ daily_use * wave + (1|child_id), data = long_boi)
summary(model)


```

```{r}
library(lattice)
library(nlme)
ctrl <- lmeControl(opt='optim');

model1 <- lme(total_score ~ daily_use, random = ~daily_use | child_id,
              data = long_boi, na.action = na.pass, control = ctrl)
summary(model1)

```

