```{r}
library(tidyverse)
library(haven)
library(lme4)
library(lmerTest)
library(nlme)
```

```{r}
## data
data <- readRDS("../data/media_long.dta")

data <- data %>%
  mutate(parent = ifelse(par_id > 30000, "Father", "Mother"))
```


# Wants to know difference between mother and father for all vairable in data set 


Difference between mom and dad for solo in wave 1
#par_id > 30,000 then it is male 
```{r}

solodiff <- aov(solo ~ par_id + wave, data = data)

summary(solodiff)
```
There is a difference between what mothers report and what fathers report for "solo" between the waves

Tukey Test for differences between parent and wave for "solo"
```{r}
summaTukeyHSD(solodiff)
```




Difference between mom and dad for coop in wave 1
#par_id > 30,000 then it is male 
```{r}

coopdiff <- aov(coop ~ par_id + wave, data = data)

summary(coopdiff)
```
There is a difference between what mothers report and what fathers report for "coop" between the waves 


Difference between mom and dad for passive in wave 1
#par_id > 30,000 then it is male 
```{r}

passivediff <- aov(passive ~ par_id + wave, data = data)

summary(passivediff)
```
There is a difference between what mothers report and what fathers report for "passive" between the waves

Difference between mom and dad for mealtime in wave 1
#par_id > 30,000 then it is male 
```{r}

mealtimediff <- aov(mealtimes ~ par_id + wave, data = data)

summary(mealtimediff)
```
There is a difference between what mothers report and what fathers report for "mealtime" between the waves


Difference between mom and dad for behavior management in wave 1
#par_id > 30,000 then it is male 
```{r}

behaviormanagementdiff <- aov(behavior_management ~ par_id + wave, data = data)

summary(behaviormanagementdiff)
```
There is a difference between what mothers report and what fathers report for "behavior managment" between the waves


Difference between mom and dad for daily use in wave 1
#par_id > 30,000 then it is male 
```{r}

dailyusediff <- aov(daily_use ~ par_id + wave, data = data)

summary(dailyusediff)
```
There is a difference between what mothers report and what fathers report for "dailyuse" between the waves


Difference between mom and dad for digital babysitting in wave 1
#par_id > 30,000 then it is male 
```{r}

digitalbabysittingdiff <- aov(digital_babysitting ~ par_id + wave, data = data)

summary(digitalbabysittingdiff)
```
There is a difference between what mothers report and what fathers report for "digital babysitting" between the waves
